---
title: "Housekeeping genes"
author: "Daniel Skubleny"
date: "07/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Housekeeping Genes

Capture the top 50 lowest variance genes and the compare their mean expression. Want to select low variance and highly expressed genes for housekeeping. 

#Across all cancer samples FSQN to affy
```{r}
all_cancer  = apply(cancer_edata, 2, var)
```
```{r}
all_cancer = sort(all_cancer, decreasing = FALSE, na.last = TRUE)
all_cancer = na.omit(all_cancer)
all_cancer = as.data.frame(all_cancer)
all_cancer$all_cancer = as.numeric(all_cancer$all_cancer)

all_cancer = all_cancer %>% top_n(-40) 

candidate = row.names(all_cancer)

#Low variance genes
lowvar = cancer_edata[, candidate]
means  = apply(lowvar, 2, mean)
```
```{r}
boxplot(lowvar, las=2)
```

#Coefficient of Variation all cancers 

```{r}
all_cancer.cv  = sapply(cancer_edata, function(x) sd(x) / mean(x) * 100)
```
```{r}
all_cancer.cv = sort(all_cancer.cv, decreasing = FALSE, na.last = TRUE)
all_cancer.cv = na.omit(all_cancer.cv)
all_cancer.cv = as.data.frame(all_cancer.cv)
all_cancer.cv$all_cancer.cv = as.numeric(all_cancer.cv$all_cancer.cv)

all_cancer.cv = all_cancer.cv %>% top_n(-100) 

candidate.cv = row.names(all_cancer.cv)

#Low variance genes
lowvar.all_cancer.cv = cancer_edata[, candidate.cv]
means.all_cancer.cv  = apply(lowvar.all_cancer.cv, 2, mean)
```
```{r}
boxplot(lowvar.all_cancer.cv, las=2, ylim = c(6,18))
```



#CV all cancer and normal samples FSQN to affy
```{r}
all_patients  =sapply(combined_edata, function(x) sd(x) / mean(x) * 100)

```
```{r}
all_patients = sort(all_patients, decreasing = FALSE, na.last = TRUE)
all_patients = na.omit(all_patients)
all_patients = as.data.frame(all_patients)
all_patients$all_patients = as.numeric(all_patients$all_patients)

all_patients = all_patients %>% top_n(-100) 

candidate.all_patients = row.names(all_patients)

#Low variance genes
lowvar.all_patients = cancer_edata[, candidate.all_patients]
means.all_patients  = apply(lowvar.all_patients, 2, mean)
```
```{r}
boxplot(lowvar.all_patients, las=2, ylim = c(0,18))
```


#CV all normals

```{r}
all_normals  = sapply(normal_edata, function(x) sd(x) / mean(x) * 100)

```
```{r}
all_normals = sort(all_normals, decreasing = FALSE, na.last = TRUE)
all_normals = na.omit(all_normals)
all_normals = as.data.frame(all_normals)
all_normals$all_normals = as.numeric(all_normals$all_normals)

all_normals = all_normals %>% top_n(-100) 

candidate.all_normals = row.names(all_normals)

#Low variance genes
lowvar.all_normals = cancer_edata[, candidate.all_normals]
means.all_normals  = apply(lowvar.all_normals, 2, mean)
```
```{r}
boxplot(lowvar.all_normals, las=2, ylim = c(6,18))
```



#CV all TCGA cancer (check a differnt distribution)

```{r}
fullTCGA_cancer = as.data.frame(fullTCGA_cancer)
tcga_cancer  = sapply(fullTCGA_cancer, function(x) sd(x) / mean(x) * 100)
```
```{r}
tcga_cancer = sort(tcga_cancer, decreasing = FALSE, na.last = TRUE)
tcga_cancer = na.omit(tcga_cancer)
tcga_cancer = as.data.frame(tcga_cancer)
tcga_cancer$tcga_cancer = as.numeric(tcga_cancer$tcga_cancer)

tcga_cancer = tcga_cancer %>% top_n(-40) 

candidate.tcga_cancer = row.names(tcga_cancer)

#Low variance genes
lowvar.tcga_cancer = fullTCGA_cancer[, candidate.tcga_cancer]
means.tcga_cancer  = apply(lowvar.tcga_cancer, 2, mean)
```
```{r}
boxplot(lowvar.tcga_cancer, las=2, ylim = c(6,18))
```
#CV all ACRG cancer (check if selected across all are just related to the FSQN target)

```{r}
log_ACRG_cancer = as.data.frame(log_ACRG_cancer)
acrg_cancer  = sapply(log_ACRG_cancer, function(x) sd(x) / mean(x) * 100)


```
```{r}
acrg_cancer = sort(acrg_cancer, decreasing = FALSE, na.last = TRUE)
acrg_cancer = na.omit(acrg_cancer)
acrg_cancer = as.data.frame(acrg_cancer)
acrg_cancer$acrg_cancer = as.numeric(acrg_cancer$acrg_cancer)

acrg_cancer = acrg_cancer %>% top_n(-40) 

candidate.acrg_cancer = row.names(acrg_cancer)

#Low variance genes
lowvar.acrg_cancer = fullTCGA_cancer[, candidate.acrg_cancer]
means.acrg_cancer  = apply(lowvar.acrg_cancer, 2, mean)
```
```{r}
boxplot(lowvar.acrg_cancer, las=2)
```




####Make TCGA target FSQN for all patients 


We will FSQN to affymterix ACRG due to it being the dominant normal class. 
```{r}
library(FSQN)
```
#FSQN normals
```{r}
#Transpose and FSQN the normals

#KUGH
data_normal_KUGH <- subset(normal_KUGH, rownames(normal_KUGH) %in% as.matrix(commongenes))
data_normal_KUGH = t(data_normal_KUGH)

#Yonsei
data_normal_yonseiMDACC <- subset(normal_yonseiMDACC, rownames(normal_yonseiMDACC) %in% as.matrix(commongenes))
data_normal_yonseiMDACC = t(data_normal_yonseiMDACC)

#ACRG
data_log_norm_ACRG <- subset(log_norm_ACRG, rownames(log_norm_ACRG) %in% as.matrix(commongenes))
data_log_norm_ACRG = t(data_log_norm_ACRG)

#TCGA
data_log_edata_norm<- subset(log_edata_norm, rownames(log_edata_norm) %in% as.matrix(commongenes))
data_log_edata_norm = t(data_log_edata_norm)
```

```{r}
#ACRG FSQN to TCGA as reference due to predominate data derived from affymetrix platform and that TME clusters were established ACRG.
set.seed(99)
target = as.matrix(data_log_edata_norm)
test = as.matrix(data_log_norm_ACRG)
fsqn_norm_ACRG.tcga = quantileNormalizeByFeature(test, target)
```

```{r}
#FSQN for remaining datasets
set.seed(99)
target = as.matrix(data_log_edata_norm)
test = as.matrix(data_normal_KUGH)
fsqn_normal_KUGH.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(data_log_edata_norm)
fsqn_normal_yonseiMDACC.tcga = quantileNormalizeByFeature(test, target)
```

```{r}
#Combine into full dataframe with all patients 
normal_edata.tcga = rbind(fsqn_norm_ACRG.tcga, data_log_edata_norm)
normal_edata.tcga = rbind(normal_edata.tcga, fsqn_normal_KUGH.tcga)
normal_edata.tcga = rbind(normal_edata.tcga, fsqn_normal_yonseiMDACC.tcga)
```


```{r}
#Add tissue type  to data frames for PCA to examine efficacy of FSQN
normal_edata.tcga = as.data.frame(normal_edata.tcga)
normal_edata.tcga$type = 'Normal'
normal_edata.tcga = normal_edata.tcga[c(9285, 1:9284)]
```


#Reduce dataset to common features for the cancers
```{r}
#Data sets - reduce to commongenes and transpose for FSQN

#ACRG
log_ACRG_cancer <- subset(log_ACRG, rownames(log_ACRG) %in% as.matrix(commongenes))
log_ACRG_cancer = t(log_ACRG_cancer)

#TCGA
fullTCGA_cancer <- subset(log_edata_fullTCGA, rownames(log_edata_fullTCGA) %in% as.matrix(commongenes))
fullTCGA_cancer = t(fullTCGA_cancer)

#Singapore 
cancer_sing <- subset(edata_sing, rownames(edata_sing) %in% as.matrix(commongenes))
cancer_sing = t(cancer_sing)

#Singapore batch B 
cancer_batchb <- subset(edata_batchb, rownames(edata_batchb) %in% as.matrix(commongenes))
cancer_batchb = t(cancer_batchb)

#Samsung 
cancer_SMC <- subset(edata_SMC, rownames(edata_SMC) %in% as.matrix(commongenes))
cancer_SMC = t(cancer_SMC)

#Shanghai
cancer_shanghai <- subset(edata_shanghai, rownames(edata_shanghai) %in% as.matrix(commongenes))
cancer_shanghai = t(cancer_shanghai)

#Yonsei
cancer_yonsei <- subset(edata_yonsei, rownames(edata_yonsei) %in% as.matrix(commongenes))
cancer_yonsei = t(cancer_yonsei)

#MDACC
cancer_MDACC <- subset(edata_MDACC, rownames(edata_MDACC) %in% as.matrix(commongenes))
cancer_MDACC = t(cancer_MDACC)

#KUGH
cancer_KUGH <- subset(edata_KUGH, rownames(edata_KUGH) %in% as.matrix(commongenes))
cancer_KUGH = t(cancer_KUGH)

#Kosin
cancer_kosin <- subset(edata_kosin, rownames(edata_kosin) %in% as.matrix(commongenes))
cancer_kosin = t(cancer_kosin)

#Yonsei MDACC
cancer_yonseiMDACC <- subset(edata_yonseiMDACC, rownames(edata_yonseiMDACC) %in% as.matrix(commongenes))
cancer_yonseiMDACC = t(cancer_yonseiMDACC)
```

#FSQN the cancers
```{r}
#TCGA FSQN to ACRG as reference due to predominate data derived from affymetrix platform and that TME clusters were established ACRG.
set.seed(99)
target = as.matrix(fullTCGA_cancer)
test = as.matrix(log_ACRG_cancer)
fsqn_cancer_ACRG.tcga = quantileNormalizeByFeature(test, target)
```

```{r}
#FSQN for remaining datasets
set.seed(99)
target = as.matrix(fullTCGA_cancer)
test = as.matrix(cancer_sing)
fsqn_cancer_sing.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_batchb)
fsqn_cancer_batchb.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_SMC)
fsqn_cancer_SMC.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_shanghai)
fsqn_cancer_shanghai.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_yonsei)
fsqn_cancer_yonsei.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_MDACC)
fsqn_cancer_MDACC.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_KUGH)
fsqn_cancer_KUGH.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_kosin)
fsqn_cancer_kosin.tcga = quantileNormalizeByFeature(test, target)

test = as.matrix(cancer_yonseiMDACC)
fsqn_cancer_yonseiMDACC.tcga = quantileNormalizeByFeature(test, target)
```

```{r}
#Combine into full dataframe with all patients 
cancer_edata.tcga = rbind(fsqn_cancer_ACRG.tcga, fullTCGA_cancer)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_sing.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_batchb.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_SMC.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_shanghai.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_yonsei.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_MDACC.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_KUGH.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_kosin.tcga)
cancer_edata.tcga = rbind(cancer_edata.tcga, fsqn_cancer_yonseiMDACC.tcga)
```

```{r}
#Add tissue type  to data frames for PCA to examine efficacy of FSQN
cancer_edata.tcga = as.data.frame(cancer_edata.tcga)
cancer_edata.tcga$type = 'Cancer'
cancer_edata.tcga = cancer_edata.tcga[c(9285, 1:9284)]
```
#Make complete dataset
```{r}
combined_edata.tcga = rbind(cancer_edata.tcga,normal_edata.tcga)
```




#Coefficient of Variation all cancers (TCGA as reference distribution)

```{r}
all_cancer.cv.tcga  = sapply(cancer_edata.tcga, function(x) sd(x) / mean(x) * 100)
```
```{r}
all_cancer.cv.tcga = sort(all_cancer.cv.tcga, decreasing = FALSE, na.last = TRUE)
all_cancer.cv.tcga = na.omit(all_cancer.cv.tcga)
all_cancer.cv.tcga = as.data.frame(all_cancer.cv.tcga)
all_cancer.cv.tcga$all_cancer.cv.tcga = as.numeric(all_cancer.cv.tcga$all_cancer.cv.tcga)

all_cancer.cv.tcga = all_cancer.cv.tcga %>% top_n(-100) 

candidate.cv.tcga = row.names(all_cancer.cv.tcga)

#Low variance genes
lowvar.all_cancer.cv.tcga = cancer_edata.tcga[, candidate.cv.tcga]
means.all_cancer.cv.tcga  = apply(lowvar.all_cancer.cv.tcga, 2, mean)
```
```{r}
boxplot(lowvar.all_cancer.cv.tcga, las=2, ylim = c(6,18))
```



#CV all cancer and normal samples FSQN to RNAseq
```{r}
all_patients.tcga  =sapply(combined_edata.tcga, function(x) sd(x) / mean(x) * 100)

```
```{r}
all_patients.tcga = sort(all_patients.tcga, decreasing = FALSE, na.last = TRUE)
all_patients.tcga = na.omit(all_patients.tcga)
all_patients.tcga = as.data.frame(all_patients.tcga)
all_patients.tcga$all_patients.tcga = as.numeric(all_patients.tcga$all_patients.tcga)

all_patients.tcga = all_patients.tcga %>% top_n(-100) 

candidate.all_patients.tcga = row.names(all_patients.tcga)

#Low variance genes
lowvar.all_patients.tcga = combined_edata.tcga[, candidate.all_patients.tcga]
means.all_patients.tcga  = apply(lowvar.all_patients.tcga, 2, mean)
```
```{r}
boxplot(lowvar.all_patients.tcga, las=2, ylim = c(0,18))
```


#CV all normals

```{r}
all_normals.tcga  = sapply(normal_edata.tcga, function(x) sd(x) / mean(x) * 100)

```
```{r}
all_normals.tcga = sort(all_normals.tcga, decreasing = FALSE, na.last = TRUE)
all_normals.tcga = na.omit(all_normals.tcga)
all_normals.tcga = as.data.frame(all_normals.tcga)
all_normals.tcga$all_normals.tcga = as.numeric(all_normals.tcga$all_normals.tcga)

all_normals.tcga = all_normals.tcga %>% top_n(-100) 

candidate.all_normals.tcga = row.names(all_normals.tcga)

#Low variance genes
lowvar.all_normals.tcga = normal_edata.tcga[, candidate.all_normals.tcga]
means.all_normals.tcga  = apply(lowvar.all_normals.tcga, 2, mean)
```
```{r}
boxplot(lowvar.all_normals.tcga, las=2, ylim = c(6,18))
```




#Intersecting genes
```{r}
intersect_acrgdist = intersect(intersect(row.names(all_cancer.cv), row.names(all_patients)),(row.names(all_normals)))
```

```{r}

intersect_tcgadist= intersect(intersect(row.names(all_cancer.cv.tcga), row.names(all_patients.tcga)),(row.names(all_normals.tcga)))
```

Pick genes - one high, medium and low expressing for each set. Plus a traditional HKG Beta Actin

#TCGA
HNRNPK
XRCC5
CTCF

#ACRG
RPL5
SUMO3
EIF4G2

#trad
ACTB
