---
title: "Singapore"
author: "Daniel Skubleny"
date: "10/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Singapore Data
data_singapore = getGEO('GSE15459')
```
```{r}
edata_singapore = as.data.frame(data_singapore[["GSE15459_series_matrix.txt.gz"]]@assayData[["exprs"]])  
pheno_singapore = as.data.frame(data_singapore[["GSE15459_series_matrix.txt.gz"]]@phenoData@data)
fdata_singapore = as.data.frame(data_singapore[["GSE15459_series_matrix.txt.gz"]]@featureData@data)
```

```{r}
exclude = c("GSM387788", "GSM387790", "GSM387793", "GSM387797", "GSM387798", "GSM387799", "GSM387844", "GSM387937")
pheno_singapore = pheno_singapore[!(row.names(pheno_singapore) %in% exclude),] #Remove excluded row names 
edata_singapore = edata_singapore[,!(colnames(edata_singapore) %in% exclude)] #Remove excluded column names
```


#Annotate 
```{r}
library(hgu133plus2.db)
annotatedsingapore = AnnotationDbi::select(hgu133plus2.db,keys = as.character(fdata_singapore$ID), columns = c("SYMBOL","ENTREZID","ENSEMBL"), keytype = "PROBEID")
```
```{r}
edata_singapore = tibble::rownames_to_column(edata_singapore, "PROBEID")
edata_singapore = merge(annotatedsingapore,edata_singapore, by.x="PROBEID")  #Merge so that SYMBOL is allocated to probes
edata_singapore = dplyr::select(edata_singapore, -c("PROBEID","ENTREZID","ENSEMBL")) #Remove PROBEID and SYMBOL.
```

Check for NAs after switching to Gene SYMBOL
```{r}
table(is.na(edata_singapore$SYMBOL))
```
```{r}
edata_singapore = edata_singapore[!is.na(edata_singapore$SYMBOL),]
```

## Check for duplicates
```{r}
table(duplicated(edata_singapore$SYMBOL))
```
```{r}
#Aggregate duplicate genes by mean
edata_singapore %>% group_by(SYMBOL) %>% summarise_all(mean) %>% data.frame() -> edata_singapore_merged
edata_singapore = edata_singapore_merged
 #Aggregate and mean duplicate SYMBOLS 
```

```{r}
edata_singapore = data.frame(edata_singapore, row.names = "SYMBOL") #Make column the row names 
```
#Check NA
```{r}
table(is.na(edata_singapore))
#No NA
```

#Now that we have our dataset lets look at our expression data distribution. Do we need to normalize? Do we have outliers?

Boxplot
```{r}
# Look at data that is not transformed vs transformed
par(mfrow=c(1,2))
boxplot(edata_singapore, col=2, range=0)
boxplot(log2(edata_singapore+1), col=2, range=0)
#Data requires log2 transform
```
Histogram
```{r}
par(mfrow=c(1,2))
hist(edata_singapore[,1],col=2)
hist(log2(edata_singapore[,1]+1),col=3)
```

Density Plot
```{r}
par(mfrow=c(1,2))
plot(density(edata_singapore[,1]),col=2)
lines(density(edata_singapore[,2]),col=3)
plot(density(log2(edata_singapore[,1]+1)),col=2)
lines(density(log2(edata_singapore[,2]+1)),col=3)
```

qqPlot
```{r}
par(mfrow=c(1,2))
qqplot(edata_singapore[,1], edata_singapore[,2],col=3)
qqplot(log2(edata_singapore[,1]+1), log2(edata_singapore[,2]+1),col=3)
```

Bland Altman Plot
```{r}
# Bland Altman Plot
mm = edata_singapore[,1] - edata_singapore[,2]
aa = edata_singapore[,1] + edata_singapore[,2]
plot(aa,mm,col=2) 
```
Let's reassess after a log2 transform 
```{r}
# Bland Altman Plot
mm = log2(edata_singapore[,1]+1) - log2(edata_singapore[,2]+1)
aa = log2(edata_singapore[,1]+1) + log2(edata_singapore[,2]+1)
plot(aa,mm,col=2) 
```
#Here we can see that the MAS 5.0 processing is not adequately creating a normalized distribution. I will process with raw CEL files instead. 

#Load packages for CEL processing 
```{r}
library(ArrayExpress)
library(oligo)
library(affy)
```

```{r}
options(timeout=999)
cel_singapore = getGEOSuppFiles('GSE15459')
```
```{r}
celpath = "/Users/GSE15459/GSE15459_RAW" #Specify path
cel_sing = ReadAffy(celfile.path = celpath)
```

#Pheno data
```{r}
pheno_sing = cel_sing@phenoData
pheno_sing 
```
```{r}
pheno_sing = pData(pheno_sing) #The sample names are the row namnes. 
```
#Feature data
```{r}
fdata_sing = cel_sing@featureData
fdata_sing
fdata_sing@data
```

#Expression data
```{r}
raw_sing = exprs(cel_sing)
```
#Retrieve probe IDs
```{r}
cdfName(cel_sing)
```
```{r}
features = featureNames(cel_sing)
length(features)
```
```{r}
length(probeNames(cel_sing))
```
#RMA normalize
```{r}
data.rma = rma(cel_sing)
edata_sing = exprs(data.rma)
```
#Fix data frame columns
```{r}
names = colnames(edata_sing) #Make columns names into a string
names = str_remove_all(names, "[.CEL.gz]") #Remove the end of string on each samples
colnames(edata_sing) = names #Rename columns 
```


```{r}
exclude = c("GSM387788", "GSM387790", "GSM387793", "GSM387797", "GSM387798", "GSM387799", "GSM387844", "GSM387937")
edata_sing = edata_sing[,!(colnames(edata_sing) %in% exclude)] #Remove excluded column names
```

#Annotate 
```{r}
library(hgu133plus2.db)
annotatedsingapore_cel = AnnotationDbi::select(hgu133plus2.db,keys = as.character(features), columns = c("SYMBOL","ENTREZID","ENSEMBL"), keytype = "PROBEID")
```
```{r}
edata_sing = as.data.frame(edata_sing)
edata_sing = tibble::rownames_to_column(edata_sing, "PROBEID")
edata_sing = merge(annotatedsingapore_cel,edata_sing, by.x="PROBEID")  #Merge so that SYMBOL is allocated to probes
edata_sing = dplyr::select(edata_sing, -c("PROBEID","ENTREZID","ENSEMBL")) #Remove PROBEID and SYMBOL.
```

Check for NAs after switching to Gene SYMBOL
```{r}
table(is.na(edata_sing$SYMBOL))
```
```{r}
edata_sing = edata_sing[!is.na(edata_sing$SYMBOL),]
```

## Check for duplicates
```{r}
table(duplicated(edata_sing$SYMBOL))
```
```{r}
#Aggregate duplicate genes by mean
edata_sing %>% group_by(SYMBOL) %>% summarise_all(mean) %>% data.frame() -> edata_sing_merged
edata_sing = edata_sing_merged
 #Aggregate and mean duplicate SYMBOLS 
```

```{r}
edata_sing = data.frame(edata_sing, row.names = "SYMBOL") #Make column the row names 
```
#Check NA
```{r}
table(is.na(edata_sing))
#No NA
```

#Exploratory data analysis of RMA normalized data. 
Boxplot
```{r}
# Look at data that is not transformed vs transformed
boxplot(edata_sing, col=2, range=0)
#Data is log2 transformed
```
Histogram
```{r}
hist(edata_sing[,1],col=2)
```

Density Plot
```{r}
plot(density(edata_sing[,1]),col=2, ylim=c(0,0.3))
lines(density(edata_sing[,2]),col=3)
```

qqPlot
```{r}
qqplot(edata_sing[,1], edata_sing[,2],col=3)
```

Bland Altman Plot
```{r}
# Bland Altman Plot
mm = edata_sing[,1] - edata_sing[,2]
aa = edata_sing[,1] + edata_sing[,2]
plot(aa,mm,col=2) 
```

#Remove low expression genes 
```{r}
mediansingapore = rowMedians(as.matrix(edata_sing))
hist(mediansingapore, breaks = 200)
```
```{r}
hist(mediansingapore, breaks = 200, xlim = c(3,6.5))
abline(v=3.7, lwd=3)
#Zoom into data and determine cut-off point
```
```{r}
hist(mediansingapore, breaks = 200)
abline(v=3.7, lwd=3)
```

```{r}
#Remove low expression genes
mediansingapore = as.data.frame(mediansingapore)
mediansingapore = mediansingapore > 3.7
edata_sing = edata_sing[mediansingapore,]
```


#Quantile Normalization 

```{r}
#Check if quantile normalization is performed
colramp = colorRampPalette(c(3,"white",2))(20)
plot(density(edata_sing[,1]),col=colramp[1],lwd=1,ylim=c(0,.35))
for(i in 2:109){lines(density(edata_sing[,i]),lwd=1,col=colramp[i])}
#After annotation there are a few issues. I will be able to correct these with FSQN. 
```




