---
title: "Singapore batch B"
author: "Daniel Skubleny"
date: "11/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
#Singapore Batch B Data
data_batchb_sing = getGEO('GSE34942')
data_batchb_supp = getGEOSuppFiles('GSE34942')
```

```{r}
#Extract pheno and fdata from the main GEO series
pheno_batchb_sing = as.data.frame(data_batchb_sing[["GSE34942_series_matrix.txt.gz"]]@phenoData@data)
fdata_batchb_sing = as.data.frame(data_batchb_sing[["GSE34942_series_matrix.txt.gz"]]@featureData@data)
```

#Load packages for CEL processing 
```{r}
library(ArrayExpress)
library(oligo)
library(affy)
```
```{r}
View(data_batchb_supp) 
```

```{r}
celpath_batchb = "/Users/GSE34942/GSE34942_RAW" #Specify path
cel_batchb = ReadAffy(celfile.path = celpath_batchb) 
```

#Pheno data
```{r}
pheno_batchb = cel_batchb@phenoData
pheno_batchb 
```
```{r}
pheno_batchb = pData(pheno_batchb) #The sample names are the row namnes. 
```
#Feature data
```{r}
fdata_batchb = cel_batchb@featureData
fdata_batchb
fdata_batchb@data
```

#Expression data
```{r}
raw_batchb = exprs(cel_batchb)
```
#Retrieve probe IDs
```{r}
cdfName(cel_batchb)
```
```{r}
features_batchb = featureNames(cel_batchb)
length(features_batchb)
```
```{r}
length(probeNames(cel_batchb))
```
#RMA normalize
```{r}
data.rma_batchb = rma(cel_batchb)
edata_batchb = exprs(data.rma_batchb)
```
#Fix data frame columns
```{r}
names_batchb = rownames(pheno_batchb_sing) #Make columns names into a string
colnames(edata_batchb) = names_batchb #Rename columns 
```


#Annotate 
```{r}
library(hgu133plus2.db)
annotatedbatchb = AnnotationDbi::select(hgu133plus2.db,keys = as.character(features_batchb), columns = c("SYMBOL","ENTREZID","ENSEMBL"), keytype = "PROBEID")
```
```{r}
edata_batchb = as.data.frame(edata_batchb)
edata_batchb = tibble::rownames_to_column(edata_batchb, "PROBEID")
edata_batchb = merge(annotatedbatchb,edata_batchb, by.x="PROBEID")  #Merge so that SYMBOL is allocated to probes
edata_batchb = dplyr::select(edata_batchb, -c("PROBEID","ENTREZID","ENSEMBL")) #Remove PROBEID and SYMBOL.
```

Check for NAs after switching to Gene SYMBOL
```{r}
table(is.na(edata_batchb$SYMBOL))
```
```{r}
edata_batchb = edata_batchb[!is.na(edata_batchb$SYMBOL),]
```

## Check for duplicates
```{r}
table(duplicated(edata_batchb$SYMBOL))
```
```{r}
#Aggregate duplicate genes by mean
edata_batchb %>% group_by(SYMBOL) %>% summarise_all(mean) %>% data.frame() -> edata_batchb_merged
edata_batchb = edata_batchb_merged
 #Aggregate and mean duplicate SYMBOLS 
```

```{r}
edata_batchb = data.frame(edata_batchb, row.names = "SYMBOL") #Make column the row names 
```
#Check NA
```{r}
table(is.na(edata_batchb))
#No NA
```


#Exploratory data analysis of RMA normalized data. 
Boxplot
```{r}
# Look at data that is not transformed vs transformed
boxplot(edata_batchb, col=2, range=0)
#Data is log2 transformed
```
Histogram
```{r}
hist(edata_batchb[,1],col=2)
```

Density Plot
```{r}
plot(density(edata_batchb[,1]),col=2, ylim=c(0,0.3))
lines(density(edata_batchb[,2]),col=3)
```

qqPlot
```{r}
qqplot(edata_batchb[,1], edata_batchb[,2],col=3)
```

Bland Altman Plot
```{r}
# Bland Altman Plot
mm = edata_batchb[,1] - edata_batchb[,2]
aa = edata_batchb[,1] + edata_batchb[,2]
plot(aa,mm,col=2) 
```

#Remove low expression genes 
```{r}
medianbatchb = rowMedians(as.matrix(edata_batchb))
hist(medianbatchb, breaks = 200)
```
```{r}
hist(medianbatchb, breaks = 200, xlim = c(1.5,7))
abline(v=4.85, lwd=3)
#Zoom into data and determine cut-off point
```
```{r}
hist(medianbatchb, breaks = 200)
abline(v=4.85, lwd=3)
```

```{r}
#Remove low expression genes
medianbatchb = as.data.frame(medianbatchb)
medianbatchb = medianbatchb > 4.85
edata_batchb = edata_batchb[medianbatchb,]
```


#Quantile Normalization 

```{r}
#Check if quantile normalization is performed
colramp = colorRampPalette(c(3,"white",2))(20)
plot(density(edata_batchb[,1]),col=colramp[1],lwd=1,ylim=c(0,.35))
for(i in 2:50){lines(density(edata_batchb[,i]),lwd=1,col=colramp[i])}
#Ready for downstream analysis. 
```










