---
title: "Clinical data"
author: "Daniel Skubleny"
date: "14/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(TCGAbiolinks)
library(readxl)
```
#Will make clinical data for survival analysis 
```{r}
#Data dictionary
#OS_status = 1 = alive/censored, 2=dead 
#PFS_status = 1 = no progression/censored, 2 = progression


```
#TCGA
```{r}
#Import full TCGA phenotype data
pheno_tcga <- read.delim("~/Documents/PhD/Gastric cancer genomic Data/stad_tcga_pan_can_atlas_2018/data_clinical_patient.txt", comment.char="#")
```
```{r}
pheno_tcga$study = 'TCGA'
pheno_tcga$RFS_status = NA
pheno_tcga$RFS_time = NA
pheno_tcga$DFS_status = NA
pheno_tcga$DFS_time = NA

colnames(pheno_tcga)[which(names(pheno_tcga) == "PATIENT_ID")] <- "patient_id"
colnames(pheno_tcga)[which(names(pheno_tcga) == "AGE")] <- "age"
colnames(pheno_tcga)[which(names(pheno_tcga) == "SEX")] <- "sex"
colnames(pheno_tcga)[which(names(pheno_tcga) == "AJCC_PATHOLOGIC_TUMOR_STAGE")] <- "stage"
colnames(pheno_tcga)[which(names(pheno_tcga) == "RACE")] <- "race"
colnames(pheno_tcga)[which(names(pheno_tcga) == "OS_STATUS")] <- "OS_status"
colnames(pheno_tcga)[which(names(pheno_tcga) == "OS_MONTHS")] <- "OS_time"
colnames(pheno_tcga)[which(names(pheno_tcga) == "PFS_STATUS")] <- "PFS_status"
colnames(pheno_tcga)[which(names(pheno_tcga) == "PFS_MONTHS")] <- "PFS_time"

pheno_tcga$stage = na_if(pheno_tcga$stage, '')
pheno_tcga$race = na_if(pheno_tcga$race, '')

pheno_tcga = dplyr::select(pheno_tcga, c("patient_id", "age", "study", "sex", "stage", "race", "OS_status", "OS_time","RFS_status", "RFS_time","PFS_status", "PFS_time","DFS_status", "DFS_time" ))
```
```{r}
query <- GDCquery(project = "TCGA-STAD", 
                  data.category = "Clinical",
                  data.type = "Clinical Supplement", 
                  data.format = "BCR Biotab")
GDCdownload(query)
```
```{r}
stad.clinical.BCRtab.all <- GDCprepare(query)
stad.patient = stad.clinical.BCRtab.all[["clinical_patient_stad"]]
stad.patient = stad.patient[-(1:2),]
```





```{r}
#Split histology into Lauren class and WHO class
stad.patient$lauren_class <- ifelse(grepl("Intestinal", stad.patient$histologic_diagnosis, ignore.case = T), "Intestinal", ifelse(grepl("Diffuse", stad.patient$histologic_diagnosis, ignore.case = T), "Diffuse", ifelse(grepl("Discrepancy", stad.patient$histologic_diagnosis, ignore.case = T), "NA", ifelse(grepl("Not Available", stad.patient$histologic_diagnosis, ignore.case = T), "NA", "Other"))))

stad.patient$who_pathology <- ifelse(grepl("NOS", stad.patient$histologic_diagnosis, ignore.case = T), "NOS", ifelse(grepl("Tubular", stad.patient$histologic_diagnosis, ignore.case = T), "Tubular", ifelse(grepl("Mucinous", stad.patient$histologic_diagnosis, ignore.case = T), "Mucinous", ifelse(grepl("Discrepancy", stad.patient$histologic_diagnosis, ignore.case = T), "NA", ifelse(grepl("Not Available", stad.patient$histologic_diagnosis, ignore.case = T), "NA", ifelse(grepl("Papillary", stad.patient$histologic_diagnosis, ignore.case = T), "Papillary", ifelse(grepl("Signet", stad.patient$histologic_diagnosis, ignore.case = T), "Signet Ring", "Other")))))))


```
```{r}
colnames(stad.patient)[which(names(stad.patient) == "bcr_patient_barcode")] <- "patient_id"
colnames(stad.patient)[which(names(stad.patient) == "tumor_grade")] <- "grade"
colnames(stad.patient)[which(names(stad.patient) == "tumor_sample_procurement_country")] <- "country"

##Removed
#colnames(stad.patient)[which(names(stad.patient) == "radiation_treatment_adjuvant")] <- "radiation"
#colnames(stad.patient)[which(names(stad.patient) == "pharmaceutical_tx_adjuvant")] <- "chemotherapy"
###Removed
colnames(stad.patient)[which(names(stad.patient) == "anatomic_neoplasm_subdivision")] <- "tumour_location"

stad.patient = dplyr::select(stad.patient, c("patient_id", "grade", "country", "tumour_location", "lauren_class", "who_pathology"))
```


##ASSESS STAD DRUG DATA SPECIFICALLY and the V1.0. 
Here we know that more patients recieved chemo than recorded in the pharmaceutical_tx_adjuvant variable in the clinical dataset. However we used the pharmaceutical_tx_adjuvant variable because it states yes or no. 

Overall we will concatenate the the clinical_drug_stad and clinical_follow_up_v1.0_stad. And we will use the clinical_follow_up_v1.0_stad for radiotherapy 
```{r}
stad.clinical.drug = stad.clinical.BCRtab.all[["clinical_drug_stad"]]


stad.clinical.drug_check = stad.clinical.drug[stad.clinical.drug$pharmaceutical_therapy_type == "Chemotherapy", ]

stad.clinical.drug_check = stad.clinical.drug_check[!duplicated(stad.clinical.drug_check$bcr_patient_barcode),]
length(unique(stad.clinical.drug_check$bcr_patient_barcode))
```
#NEW TCGA CHEMO
```{r}
stad_chemo = stad.clinical.BCRtab.all[["clinical_follow_up_v1.0_stad"]]
stad_chemo = stad_chemo[-(1:2),]
stad_chemo = dplyr::select(stad_chemo, c("bcr_patient_barcode", "pharmaceutical_tx_adjuvant", "radiation_treatment_adjuvant"))
stad.patient = stad.clinical.BCRtab.all[["clinical_patient_stad"]]
stad.patient = stad.patient[-(1:2),]
stad_chemo_two = dplyr::select(stad.patient, c("bcr_patient_barcode", "pharmaceutical_tx_adjuvant", "radiation_treatment_adjuvant"))
stad_chemo_new = merge(stad_chemo, stad_chemo_two, by = "bcr_patient_barcode", all=TRUE)

#Need to code chemo vs chemo and rad vs rad. yes if yes and not available etc. Yes if both are yes. Eliminate if discrepancy. 

table(stad_chemo_new$pharmaceutical_tx_adjuvant.x,stad_chemo_new$pharmaceutical_tx_adjuvant.y) #Here there is only one updated discrepancy for yes chemo previously and the new v1.0 saying no chemo. 

table(stad_chemo_new$radiation_treatment_adjuvant.x,stad_chemo_new$radiation_treatment_adjuvant.y) #Here there is no discrepancy for the new no vs old yes. But there are some old no that now became yes. This is ok. We will use v1.0.

stad.clinical.drug_check = stad.clinical.drug_check[!duplicated(stad.clinical.drug_check$bcr_patient_barcode), ]

stad_chemo_new_2 = merge(stad_chemo_new, stad.clinical.drug_check, by = "bcr_patient_barcode", all=TRUE)
stad_chemo_new_2 = stad_chemo_new_2[!duplicated(stad_chemo_new_2$bcr_patient_barcode), ]

stad_chemo_new_2["pharmaceutical_therapy_type"][is.na(stad_chemo_new_2["pharmaceutical_therapy_type"])] <- "Unknown"
stad_chemo_new_2["pharmaceutical_tx_adjuvant.x"][is.na(stad_chemo_new_2["pharmaceutical_tx_adjuvant.x"])] <- "Unknown"


#After removing duplicates
table(stad_chemo_new_2$pharmaceutical_tx_adjuvant.x)
table(stad_chemo_new_2$pharmaceutical_tx_adjuvant.y)
table(stad_chemo_new_2$pharmaceutical_therapy_type)

table(stad_chemo_new_2$pharmaceutical_tx_adjuvant.x,stad_chemo_new_2$pharmaceutical_therapy_type)
#Here we see that chemotherapy data exists for a number of missing data pieces in the V.1. 


stad_chemo_new_2$new_rad <- stad_chemo_new_2$radiation_treatment_adjuvant.x

stad_chemo_new_2$new_chemo <- with(stad_chemo_new_2, ifelse(
pharmaceutical_therapy_type=="Chemotherapy", "YES", ifelse(
  pharmaceutical_tx_adjuvant.x=="YES" & pharmaceutical_therapy_type=="Unknown", "YES", ifelse(
    pharmaceutical_tx_adjuvant.x=="NO" & pharmaceutical_therapy_type=="Unknown", "NO", NA))))
    


colnames(stad_chemo_new_2)[which(names(stad_chemo_new_2) == "bcr_patient_barcode")] <- "patient_id"
colnames(stad_chemo_new_2)[which(names(stad_chemo_new_2) == "new_chemo")] <- "chemotherapy"
colnames(stad_chemo_new_2)[which(names(stad_chemo_new_2) == "new_rad")] <- "radiation"

stad_chemo_new_2 = dplyr::select(stad_chemo_new_2, c("patient_id", "radiation", "chemotherapy"))
```

####Add in new therapy data 
```{r}
stad.patient = merge(stad.patient,stad_chemo_new_2, by="patient_id")
```

```{r}
#Extract EBV ISH 
ebv_ish <- read.delim("~/Documents/PhD/Gastric cancer genomic Data/stad_tcga_pub/data_clinical_patient.txt", comment.char="#")
colnames(ebv_ish)[which(names(ebv_ish) == "PATIENT_ID")] <- "patient_id"
colnames(ebv_ish)[which(names(ebv_ish) == "EBV_PRESENT")] <- "ebv_ish"
ebv_ish = dplyr::select(ebv_ish, c("patient_id", "ebv_ish", "SIGNET_RING"))

ebv_ish$ebv_ish <- str_replace_all(ebv_ish$ebv_ish, c("0" = "Negative", "1" = "Positive"))
```
```{r}
#Combine tcga pdata dataframes
pdata_tcga = merge(pheno_tcga,stad.patient, by.x="patient_id", all=TRUE)
##pdata_tcga = merge(pdata_tcga,stad_chemo_new, by.x="patient_id", all=TRUE)##Removed
pdata_tcga = merge(pdata_tcga,ebv_ish, by.x="patient_id", all=TRUE)
```
```{r}
pdata_tcga$signet_ring <- ifelse(grepl("Signet", pdata_tcga$who_pathology, ignore.case = T), "Signet Ring", ifelse(grepl("1", pdata_tcga$SIGNET_RING, ignore.case = T), "Signet Ring", "No"))

pdata_tcga = dplyr::select(pdata_tcga, -c("who_pathology", "SIGNET_RING"))


col_order <- c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time" )
pdata_tcga <- pdata_tcga[, col_order]
```
```{r}
#Tidy up data labels and strings
pdata_tcga$OS_status <- str_replace_all(pdata_tcga$OS_status, c("0:LIVING" = "1", "1:DECEASED" = "2"))
pdata_tcga$PFS_status <- str_replace_all(pdata_tcga$PFS_status, c("0:CENSORED" = "1", "1:PROGRESSION" = "2"))

pdata_tcga$stage <- str_replace_all(pdata_tcga$stage, c("STAGE I" = "I", "STAGE IA" = "I", "STAGE IB" = "I", "STAGE II" = "II", "STAGE IIA" = "II", "STAGE IIB" = "II", "STAGE III" = "III", "STAGE IIIA" = "III", "STAGE IIIB" = "III", "STAGE IIIC" = "III", "STAGE IV" = "IV"))

pdata_tcga$stage <- str_replace_all(pdata_tcga$stage, c("I" = "I", "IA" = "I", "IB" = "I", "II" = "II", "IIA" = "II", "IIB" = "II", "III" = "III", "IIIA" = "III", "IIIB" = "III", "IIIC" = "III", "IV" = "IV"))
```

#ACRG Clinical Data

```{r}
#ACRG Data
options(timeout=100)
data_ACRG = getGEO('GSE62254')
```
```{r}
pheno_ACRG <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/ACRG data/pheno_data.xls", col_types = c("numeric", "numeric", "text", "text", "text", "numeric", "text", "text", "text", "text", "numeric","numeric", "numeric", "numeric", "text", "numeric", "text", "text", "numeric", "numeric", "text", "text", "numeric", "numeric", "text", "text", "numeric", "text", "numeric", "numeric", "numeric", "text", "numeric", "date", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "text", "numeric", "date", "numeric", "numeric", "numeric", "numeric"))
```
```{r}
pdata_acrg = (data_ACRG[["GSE62254_series_matrix.txt.gz"]]@phenoData@data)
pdata_acrg = pdata_acrg <- tibble::rownames_to_column(pdata_acrg, "patient_id")
colnames(pdata_acrg)[which(names(pdata_acrg) == "patient:ch1")] <- "Tumor ID"
pdata_acrg = dplyr::select(pdata_acrg, c("Tumor ID", "patient_id"))
```
```{r}
pheno_ACRG = merge(pdata_acrg,pheno_ACRG, by.x="Tumor ID", all=TRUE)
```
```{r}
pheno_ACRG$study = 'ACRG'
pheno_ACRG$race = NA
pheno_ACRG$grade = NA
pheno_ACRG$country = 'Korea'
pheno_ACRG$RFS_status = NA
pheno_ACRG$RFS_time = NA
pheno_ACRG$PFS_status = NA
pheno_ACRG$PFS_time = NA
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "EBV ISH\n0: negative\n1: positive\nNA: Not available (no available tumor blocks)")] <- "ebv_ish"
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "Code_site")] <- "tumour_location"
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "Lauren")] <- "lauren_class"
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "WHO 1=w/d adeno\n2=m/d adeno\n3=p/d adeno\n4=signet ring\n5= mucinous\n6=papillary adeno\n7=adenosquamous\n8=undifferentiated ca\n9=hepatoid adenoca\n10=tubular adenoca\n11=others (text)")] <- "who_pathology"
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "WHO_simple")] <- "SIGNET_RING"
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "ADJ CTx. Description")] <- "chemotherapy"
colnames(pheno_ACRG)[which(names(pheno_ACRG) == "Adjuvant  CCRT CYCLE")] <- "radiation"

pheno_ACRG$ebv_ish <- str_replace_all(pheno_ACRG$ebv_ish, c("0" = "Negative", "1" = "Positive")) 
pheno_ACRG$signet_ring <- ifelse(grepl("signet", pheno_ACRG$SIGNET_RING, ignore.case = T), "Signet Ring", "NA")
pheno_ACRG$radiation[is.na(pheno_ACRG$radiation)] = 0
pheno_ACRG$radiation = ifelse(grepl("0", pheno_ACRG$radiation, ignore.case = T), "No", "Yes")
pheno_ACRG$chemotherapy[is.na(pheno_ACRG$chemotherapy)] = 0
pheno_ACRG$chemotherapy = ifelse(grepl("0", pheno_ACRG$chemotherapy, ignore.case = T), "No", "Yes")
```

```{r}
pheno_ACRG = dplyr::select(pheno_ACRG, c("patient_id", "study", "age", "sex", "grade", "race", "lauren_class", "signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "RFS_status", "RFS_time","PFS_status","PFS_time"))
```
```{r}
acrg_clinical <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/MP:EP Paper/41467_2018_4179_MOESM5_ESM.xlsx", sheet = "ACRG")
```
```{r}
colnames(acrg_clinical)[which(names(acrg_clinical) == "GEO_ID")] <- "patient_id"
colnames(acrg_clinical)[which(names(acrg_clinical) == "Stage")] <- "stage"
colnames(acrg_clinical)[which(names(acrg_clinical) == "Recur")] <- "DFS_status"
colnames(acrg_clinical)[which(names(acrg_clinical) == "DFS.m")] <- "DFS_time"
colnames(acrg_clinical)[which(names(acrg_clinical) == "Death")] <- "OS_status"
colnames(acrg_clinical)[which(names(acrg_clinical) == "OS.m")] <- "OS_time"

acrg_clinical = dplyr::select(acrg_clinical, c("patient_id", "stage", "DFS_status", "DFS_time", "OS_status", "OS_time"))

```
```{r}
#Combine acrg pdata dataframes
pheno_ACRG = merge(pheno_ACRG,acrg_clinical, by.x="patient_id", all=TRUE)
pheno_ACRG <- pheno_ACRG[, col_order]
```
```{r}
#Clean up ACRG dataframe
pheno_ACRG <- pheno_ACRG %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_ACRG <- pheno_ACRG %>% mutate(DFS_status = ifelse(DFS_status == "0",1,2))
pheno_ACRG$sex <- str_replace_all(pheno_ACRG$sex, c("M" = "Male", "F" = "Female"))
pheno_ACRG$lauren_class <- str_replace_all(pheno_ACRG$lauren_class, c("intestinal" = "Intestinal", "diffuse" = "Diffuse", "mixed" = "Mixed"))
```


#MDACC
```{r}
pheno_MDACC = pheno_MDACC <- tibble::rownames_to_column(pheno_MDACC, "patient_id")
pheno_MDACC$study = 'MDACC'
pheno_MDACC$race = NA
pheno_MDACC$lauren_class = NA
pheno_MDACC$signet_ring = NA
pheno_MDACC$tumour_location = NA
pheno_MDACC$ebv_ish = NA
pheno_MDACC$country = NA
pheno_MDACC$RFS_status = NA
pheno_MDACC$RFS_time = NA
pheno_MDACC$PFS_status = NA
pheno_MDACC$PFS_time = NA
pheno_MDACC$DFS_status = NA
pheno_MDACC$DFS_time = NA

colnames(pheno_MDACC)[which(names(pheno_MDACC) == "gender:ch1")] <- "sex"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "grade:ch1")] <- "grade"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "baseline stage:ch1")] <- "stage"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "sample_id:ch1")] <- "GEO ID"

pheno_MDACC = dplyr::select(pheno_MDACC, c("patient_id", "study", "sex", "stage", "grade", "race", "lauren_class", "signet_ring", "tumour_location", "ebv_ish", "country", "RFS_status", "RFS_time","PFS_status","PFS_time", "DFS_status", "DFS_time", "GEO ID"))
```
```{r}
mdacc_clinical <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/MP:EP Paper/41467_2018_4179_MOESM5_ESM.xlsx", sheet = "MDACC")

pheno_MDACC = merge(pheno_MDACC,mdacc_clinical, by.x="GEO ID", all=TRUE)

colnames(pheno_MDACC)[which(names(pheno_MDACC) == "Age")] <- "age"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "Death (1=yes, 0=no)")] <- "OS_status"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "OS.m")] <- "OS_time"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "Chemotherapy")] <- "chemotherapy"
colnames(pheno_MDACC)[which(names(pheno_MDACC) == "RadiationTherapy")] <- "radiation"

pheno_MDACC = dplyr::select(pheno_MDACC, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))

pheno_MDACC <- pheno_MDACC[, col_order]
```
```{r}

pheno_MDACC <- pheno_MDACC %>% mutate(OS_status = ifelse(OS_status == "0",1,2))

pheno_MDACC$stage <- str_replace_all(pheno_MDACC$stage, c("I" = "I", "IA" = "I", "IB" = "I", "II" = "II", "IIA" = "II", "IIB" = "II", "III" = "III", "IIIA" = "III", "IIIB" = "III", "IIIC" = "III", "IV" = "IV"))
```
#Samsung
```{r}
clinical_SMC <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/MP:EP Paper/41467_2018_4179_MOESM5_ESM.xlsx", sheet = "SMC")
clinical_SMC = clinical_SMC[order(clinical_SMC$Patients_ID),]
```
```{r}
pheno_SMC = cbind(clinical_SMC,pheno_SMC)
```
```{r}
pheno_SMC = pheno_SMC <- tibble::rownames_to_column(pheno_SMC, "patient_id")

pheno_SMC$study = 'Samsung'
pheno_SMC$race = NA
pheno_SMC$grade = NA
pheno_SMC$signet_ring = NA
pheno_SMC$ebv_ish = NA
pheno_SMC$country = 'Korea'
pheno_SMC$PFS_status = NA
pheno_SMC$PFS_time = NA
pheno_SMC$DFS_status = NA
pheno_SMC$DFS_time = NA
pheno_SMC$radiation = NA


colnames(pheno_SMC)[which(names(pheno_SMC) == "Sex")] <- "sex"
colnames(pheno_SMC)[which(names(pheno_SMC) == "Age")] <- "age"
colnames(pheno_SMC)[which(names(pheno_SMC) == "AJCC.stage")] <- "stage"
colnames(pheno_SMC)[which(names(pheno_SMC) == "Location")] <- "tumour_location"
colnames(pheno_SMC)[which(names(pheno_SMC) == "Lauren")] <- "lauren_class"
colnames(pheno_SMC)[which(names(pheno_SMC) == "Death (1=yes, 0=no)")] <- "OS_status"
colnames(pheno_SMC)[which(names(pheno_SMC) == "OS.m")] <- "OS_time"
colnames(pheno_SMC)[which(names(pheno_SMC) == "Recurrence (1=yes, 0=no)")] <- "RFS_status"
colnames(pheno_SMC)[which(names(pheno_SMC) == "RFS.m")] <- "RFS_time"
colnames(pheno_SMC)[which(names(pheno_SMC) == "Adjuvant.chemo")] <- "chemotherapy"

pheno_SMC = dplyr::select(pheno_SMC, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))

pheno_SMC <- pheno_SMC[, col_order]
```
```{r}
#Clean up data
pheno_SMC <- pheno_SMC %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_SMC <- pheno_SMC %>% mutate(RFS_status = ifelse(RFS_status == "0",1,2))
pheno_SMC$sex <- str_replace_all(pheno_SMC$sex, c("M" = "Male", "F" = "Female"))
pheno_SMC$lauren_class <- str_replace_all(pheno_SMC$lauren_class, c("intestinal" = "Intestinal", "diffuse" = "Diffuse", "mixed"="Mixed"))
```
#KUGH 

```{r}
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "patient:ch1")] <- "Patients_ID"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "geo_accession")] <- "patient_id"

```
```{r}
clinical_KUGH <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/MP:EP Paper/41467_2018_4179_MOESM5_ESM.xlsx", sheet = "KUGH")
pheno_KUGH = merge(pheno_KUGH,clinical_KUGH, by.x="Patients_ID")
```
```{r}

pheno_KUGH$study = 'KUGH'
pheno_KUGH$race = NA
pheno_KUGH$grade = NA
pheno_KUGH$signet_ring = NA
pheno_KUGH$ebv_ish = NA
pheno_KUGH$country = NA
pheno_KUGH$PFS_status = NA
pheno_KUGH$PFS_time = NA
pheno_KUGH$DFS_status = NA
pheno_KUGH$DFS_time = NA
pheno_KUGH$radiation = NA

colnames(pheno_KUGH)[which(names(pheno_KUGH) == "adjuvant chemotherapy (1=yes, 0=no, na=not available):ch1")] <- "chemotherapy"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "lauren classification:ch1")] <- "lauren_class"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "Age")] <- "age"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "gender:ch1")] <- "sex"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "Location")] <- "tumour_location"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "ajcc stage:ch1")] <- "stage"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "Death (1=yes, 0=no)")] <- "OS_status"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "OS.m")] <- "OS_time"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "Recurrence (1=yes, 0=no)")] <- "RFS_status"
colnames(pheno_KUGH)[which(names(pheno_KUGH) == "RFS.m")] <- "RFS_time"

pheno_KUGH = dplyr::select(pheno_KUGH, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))

pheno_KUGH <- pheno_KUGH[, col_order]
```
```{r}
#Clean up data
pheno_KUGH <- pheno_KUGH %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_KUGH <- pheno_KUGH %>% mutate(RFS_status = ifelse(RFS_status == "0",1,2))
pheno_KUGH$chemotherapy <- str_replace_all(pheno_KUGH$chemotherapy, c("0" = "No", "1" = "Yes"))
pheno_KUGH$sex <- str_replace_all(pheno_KUGH$sex, c("M" = "Male", "F" = "Female"))
pheno_KUGH$stage <- str_replace_all(pheno_KUGH$stage, c("1" = "I", "2" = "II", "3" = "III", "4" = "IV"))

```
#KOSIN
```{r}
colnames(pheno_kosin)[which(names(pheno_kosin) == "patient:ch1")] <- "Patients_ID"
colnames(pheno_kosin)[which(names(pheno_kosin) == "geo_accession")] <- "patient_id"
```
```{r}
Patients_ID = sub("T", "", pheno_kosin$Patients_ID)
Patients_ID = str_replace_all(Patients_ID, "[[:punct:]]", "")
pheno_kosin$Patients_ID = Patients_ID
```
```{r}
clinical_kosin <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/MP:EP Paper/41467_2018_4179_MOESM5_ESM.xlsx", sheet = "KUCM")
pheno_kosin = merge(pheno_kosin,clinical_kosin, by.x="Patients_ID")
```
```{r}

pheno_kosin$study = 'Kosin'
pheno_kosin$race = NA
pheno_kosin$grade = NA
pheno_kosin$signet_ring = NA
pheno_kosin$ebv_ish = NA
pheno_kosin$country = NA
pheno_kosin$PFS_status = NA
pheno_kosin$PFS_time = NA
pheno_kosin$DFS_status = NA
pheno_kosin$DFS_time = NA
pheno_kosin$radiation = NA

colnames(pheno_kosin)[which(names(pheno_kosin) == "adjuvant chemotherapy (1=yes, 0=no, na=not available):ch1")] <- "chemotherapy"
colnames(pheno_kosin)[which(names(pheno_kosin) == "lauren classification:ch1")] <- "lauren_class"
colnames(pheno_kosin)[which(names(pheno_kosin) == "Age")] <- "age"
colnames(pheno_kosin)[which(names(pheno_kosin) == "gender:ch1")] <- "sex"
colnames(pheno_kosin)[which(names(pheno_kosin) == "Location")] <- "tumour_location"
colnames(pheno_kosin)[which(names(pheno_kosin) == "ajcc stage:ch1")] <- "stage"
colnames(pheno_kosin)[which(names(pheno_kosin) == "Death (1=yes, 0=no)")] <- "OS_status"
colnames(pheno_kosin)[which(names(pheno_kosin) == "OS.m")] <- "OS_time"
colnames(pheno_kosin)[which(names(pheno_kosin) == "Recurrence (1=yes, 0=no)")] <- "RFS_status"
colnames(pheno_kosin)[which(names(pheno_kosin) == "RFS.m")] <- "RFS_time"

pheno_kosin = dplyr::select(pheno_kosin, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))

pheno_kosin <- pheno_kosin[, col_order]
```
```{r}
#Clean up data
pheno_kosin <- pheno_kosin %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_kosin <- pheno_kosin %>% mutate(RFS_status = ifelse(RFS_status == "0",1,2))
pheno_kosin$chemotherapy <- str_replace_all(pheno_kosin$chemotherapy, c("0" = "No", "1" = "Yes"))
pheno_kosin$sex <- str_replace_all(pheno_kosin$sex, c("M" = "Male", "F" = "Female"))
pheno_kosin$stage <- str_replace_all(pheno_kosin$stage, c("1" = "I", "2" = "II", "3" = "III", "4" = "IV"))
pheno_kosin$lauren_class <- str_replace_all(pheno_kosin$lauren_class, c("intestinal" = "Intestinal", "diffuse" = "Diffuse", "mixed"="Mixed"))
```

#Signapore
```{r}
clinical_singapore <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/Singapore and singapore batch b cohort/GSE15459_outcome.xls")
```
```{r}
clinical_singapore$study = 'Singapore'
clinical_singapore$race = NA
clinical_singapore$grade = NA
clinical_singapore$signet_ring = NA
clinical_singapore$tumour_location = NA
clinical_singapore$ebv_ish = NA
clinical_singapore$country = 'Singapore'
clinical_singapore$PFS_status = NA
clinical_singapore$PFS_time = NA
clinical_singapore$DFS_status = NA
clinical_singapore$DFS_time = NA
clinical_singapore$RFS_status = NA
clinical_singapore$RFS_time = NA
clinical_singapore$radiation = NA
clinical_singapore$chemotherapy = NA

colnames(clinical_singapore)[which(names(clinical_singapore) == "GSM ID")] <- "patient_id"
colnames(clinical_singapore)[which(names(clinical_singapore) == "Age_at_surgery")] <- "age"
colnames(clinical_singapore)[which(names(clinical_singapore) == "Gender")] <- "sex"
colnames(clinical_singapore)[which(names(clinical_singapore) == "Laurenclassification")] <- "lauren_class"
colnames(clinical_singapore)[which(names(clinical_singapore) == "Stage")] <- "stage"
colnames(clinical_singapore)[which(names(clinical_singapore) == "Overall.Survival (Months)**")] <- "OS_time"
colnames(clinical_singapore)[which(names(clinical_singapore) == "Outcome (1=dead)")] <- "OS_status"

pheno_singapore = dplyr::select(clinical_singapore, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))

pheno_singapore <- pheno_singapore[, col_order]
```
```{r}
#Clean up data
pheno_singapore <- pheno_singapore %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_singapore$stage <- str_replace_all(pheno_singapore$stage, c("1" = "I", "2" = "II", "3" = "III", "4" = "IV"))
pheno_singapore = pheno_singapore[-193,]
```


#Singapore Batch B
```{r}
clinical_batchb <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/Singapore and singapore batch b cohort/GSE34942_outcome.xls")
```
```{r}
clinical_batchb$study = 'Singapore'
clinical_batchb$race = NA
clinical_batchb$grade = NA
clinical_batchb$signet_ring = NA
clinical_batchb$tumour_location = NA
clinical_batchb$ebv_ish = NA
clinical_batchb$country = 'Singapore'
clinical_batchb$PFS_status = NA
clinical_batchb$PFS_time = NA
clinical_batchb$DFS_status = NA
clinical_batchb$DFS_time = NA
clinical_batchb$RFS_status = NA
clinical_batchb$RFS_time = NA
clinical_batchb$radiation = NA
clinical_batchb$chemotherapy = NA

colnames(clinical_batchb)[which(names(clinical_batchb) == "GSM ID")] <- "patient_id"
colnames(clinical_batchb)[which(names(clinical_batchb) == "Age_at_surgery")] <- "age"
colnames(clinical_batchb)[which(names(clinical_batchb) == "Gender")] <- "sex"
colnames(clinical_batchb)[which(names(clinical_batchb) == "Laurenclassification")] <- "lauren_class"
colnames(clinical_batchb)[which(names(clinical_batchb) == "Stage")] <- "stage"
colnames(clinical_batchb)[which(names(clinical_batchb) == "Overall.Survival (Months)**")] <- "OS_time"
colnames(clinical_batchb)[which(names(clinical_batchb) == "Outcome (1=dead)")] <- "OS_status"

pheno_batchb = dplyr::select(clinical_batchb, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))

pheno_batchb <- pheno_batchb[, col_order]
```
```{r}
#Clean up data
pheno_batchb <- pheno_batchb %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_batchb$stage <- str_replace_all(pheno_batchb$stage, c("1" = "I", "2" = "II", "3" = "III", "4" = "IV"))
pheno_batchb = pheno_batchb[-57,]
```

#Yonsei MDACC
```{r}
pheno_yonseiMDACC = as.data.frame(data_yonseiMDACC[["GSE13861_series_matrix.txt.gz"]]@phenoData@data)
```
```{r}
pheno_yonseiMDACC = pheno_yonseiMDACC <- tibble::rownames_to_column(pheno_yonseiMDACC, "patient_id")

Patients_ID = str_extract(pheno_yonseiMDACC$title, "YG.*" )
Patients_ID = sub("\\T.*", "T", Patients_ID)
pheno_yonseiMDACC$Patients_ID =Patients_ID


```
```{r}
clinical_yonseiMDACC <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/MP:EP Paper/41467_2018_4179_MOESM5_ESM.xlsx", sheet = "YUHS")
pheno_yonseiMDACC = merge(pheno_yonseiMDACC,clinical_yonseiMDACC, by.x="Patients_ID")
```
```{r}
pathology_yonsei <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/YONSEI (YUSH)/GSE13861_GE_MDACC_DepSysB_ClinicalInformation_update_ver2.xls")
pathology_yonsei = pathology_yonsei[,-1]
colnames(pathology_yonsei)[which(names(pathology_yonsei) == "Array ID")] <- "Patients_ID"

pheno_yonseiMDACC = merge(pheno_yonseiMDACC,pathology_yonsei, by="Patients_ID")

pheno_yonseiMDACC$study = 'Yonsei MDACC'
pheno_yonseiMDACC$race = NA
pheno_yonseiMDACC$country = NA
pheno_yonseiMDACC$radiation = NA
pheno_yonseiMDACC$ebv_ish = NA
pheno_yonseiMDACC$PFS_status = NA
pheno_yonseiMDACC$PFS_time = NA
pheno_yonseiMDACC$DFS_status = NA
pheno_yonseiMDACC$DFS_time = NA

colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Location.y")] <- "tumour_location"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Age.x")] <- "age"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Gender")] <- "sex"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Lauren's classification")] <- "lauren_class"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "AJCC6")] <- "stage"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Grade")] <- "pathology"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Adjuvant.chemo")] <- "chemotherapy"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Recurrence (1=yes, 0=no)")] <- "RFS_status"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "RFS.m")] <- "RFS_time"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "Death (1=yes, 0=no)")] <- "OS_status"
colnames(pheno_yonseiMDACC)[which(names(pheno_yonseiMDACC) == "OS.m")] <- "OS_time"

pheno_yonseiMDACC$pathology <- str_replace_all(pheno_yonseiMDACC$pathology, c("Moderate" = "G2", "Poorly" = "G3", "Well" = "G1"))

pheno_yonseiMDACC$signet_ring <- ifelse(grepl("Signet", pheno_yonseiMDACC$pathology, ignore.case = T), "Signet", ifelse(grepl("NA", pheno_yonseiMDACC$pathology, ignore.case = T), "NA","Other"))
                                                                                                                        
pheno_yonseiMDACC$grade <- ifelse(grepl("G1", pheno_yonseiMDACC$pathology, ignore.case = T), "G1", ifelse(grepl("G2", pheno_yonseiMDACC$pathology, ignore.case = T), "G2", ifelse(grepl("G3", pheno_yonseiMDACC$pathology, ignore.case = T), "G3", ifelse(grepl("NA", pheno_yonseiMDACC$pathology, ignore.case = T), "NA", "Other"))))                        
```
```{r}
pheno_yonseiMDACC = dplyr::select(pheno_yonseiMDACC, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))
pheno_yonseiMDACC <- pheno_yonseiMDACC[, col_order]
```
```{r}
#Clean data
pheno_yonseiMDACC <- pheno_yonseiMDACC %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
pheno_yonseiMDACC <- pheno_yonseiMDACC %>% mutate(RFS_status = ifelse(RFS_status == "0",1,2))
pheno_yonseiMDACC$lauren_class <- str_replace_all(pheno_yonseiMDACC$lauren_class, c("intestinal" = "Intestinal", "diffuse" = "Diffuse", "mixed"="Mixed"))
pheno_yonseiMDACC$signet_ring[pheno_yonseiMDACC$signet_ring == 'NA'] <- NA
pheno_yonseiMDACC$grade[pheno_yonseiMDACC$grade == 'NA'] <- NA
```
#China Shanghai 
```{r}
clinical_shanghai <- read_excel("~/Documents/PhD/Gastric cancer genomic Data/TME Score/204325_4_supp_5320157_pmcfmm.xlsx", sheet = "S12")
colnames(clinical_shanghai) = NULL
colnames(clinical_shanghai) <- clinical_shanghai[1,]
clinical_shanghai <- clinical_shanghai[-1, ] 
colnames(clinical_shanghai)[which(names(clinical_shanghai) == "ID")] <- "patient_id"


pheno_shanghai = pheno_shanghai <- tibble::rownames_to_column(pheno_shanghai, "patient_id")
pheno_shanghai = dplyr::select(pheno_shanghai, "patient_id")

pheno_shanghai = merge(pheno_shanghai,clinical_shanghai, by.x="patient_id")
```
```{r}
colnames(pheno_shanghai)[which(names(pheno_shanghai) == "OS_months")] <- "OS_time"
colnames(pheno_shanghai)[which(names(pheno_shanghai) == "OS_event")] <- "OS_status"


pheno_shanghai$study = 'Shanghai'
pheno_shanghai$age = NA
pheno_shanghai$race = NA
pheno_shanghai$sex = NA
pheno_shanghai$stage = NA
pheno_shanghai$grade = NA
pheno_shanghai$lauren_class = NA
pheno_shanghai$signet_ring = NA
pheno_shanghai$tumour_location = NA
pheno_shanghai$chemotherapy = NA
pheno_shanghai$radiation = NA
pheno_shanghai$country = 'China'
pheno_shanghai$ebv_ish = NA
pheno_shanghai$PFS_status = NA
pheno_shanghai$PFS_time = NA
pheno_shanghai$DFS_status = NA
pheno_shanghai$DFS_time = NA
pheno_shanghai$RFS_status = NA
pheno_shanghai$RFS_time = NA
```
```{r}
pheno_shanghai = dplyr::select(pheno_shanghai, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))
pheno_shanghai <- pheno_shanghai[, col_order]
```
```{r}
#Clean data
pheno_shanghai <- pheno_shanghai %>% mutate(OS_status = ifelse(OS_status == "0",1,2))

```
#Korea Yonsei
```{r}
pheno_yonsei = pheno_yonsei <- tibble::rownames_to_column(pheno_yonsei, "patient_id")

colnames(pheno_yonsei)[which(names(pheno_yonsei) == "Sex:ch1")] <- "sex"
colnames(pheno_yonsei)[which(names(pheno_yonsei) == "age:ch1")] <- "age"
colnames(pheno_yonsei)[which(names(pheno_yonsei) == "duration overall survival:ch1")] <- "OS_time"
colnames(pheno_yonsei)[which(names(pheno_yonsei) == "death:ch1")] <- "OS_status"


pheno_yonsei$study = 'Yonsei'
pheno_yonsei$race = NA
pheno_yonsei$stage = NA
pheno_yonsei$grade = NA
pheno_yonsei$lauren_class = NA
pheno_yonsei$signet_ring = NA
pheno_yonsei$tumour_location = NA
pheno_yonsei$chemotherapy = NA
pheno_yonsei$radiation = NA
pheno_yonsei$country = 'Korea'
pheno_yonsei$ebv_ish = NA
pheno_yonsei$PFS_status = NA
pheno_yonsei$PFS_time = NA
pheno_yonsei$DFS_status = NA
pheno_yonsei$DFS_time = NA
pheno_yonsei$RFS_status = NA
pheno_yonsei$RFS_time = NA
```
```{r}
pheno_yonsei = dplyr::select(pheno_yonsei, c("patient_id", "study", "age", "sex", "stage", "grade", "race", "lauren_class","signet_ring", "tumour_location", "chemotherapy", "radiation", "ebv_ish", "country", "OS_status", "OS_time", "RFS_status", "RFS_time", "PFS_status", "PFS_time","DFS_status", "DFS_time"))
pheno_yonsei <- pheno_yonsei[, col_order]
```
```{r}
#Clean data
pheno_yonsei <- pheno_yonsei %>% mutate(OS_status = ifelse(OS_status == "0",1,2))
```

#Combine into one dataframe
```{r}
#Combine into full dataframe with all patients 
survival_TCGA = rbind(pdata_tcga, pheno_ACRG)
survival_TCGA = rbind(survival_TCGA, pheno_MDACC)
survival_TCGA = rbind(survival_TCGA, pheno_SMC)
survival_TCGA = rbind(survival_TCGA, pheno_KUGH)
survival_TCGA = rbind(survival_TCGA, pheno_kosin)
survival_TCGA = rbind(survival_TCGA, pheno_singapore)
survival_TCGA = rbind(survival_TCGA, pheno_batchb)
survival_TCGA = rbind(survival_TCGA, pheno_yonseiMDACC)
survival_TCGA = rbind(survival_TCGA, pheno_shanghai)
survival_TCGA = rbind(survival_TCGA, pheno_yonsei)
```

```{r}
survival_TCGA$chemotherapy[survival_TCGA$chemotherapy == 'NA'] <- NA
survival_TCGA$chemotherapy[survival_TCGA$chemotherapy == '[Not Available]'] <- NA
survival_TCGA$chemotherapy[survival_TCGA$chemotherapy == '[Unknown]'] <- NA

survival_TCGA$chemotherapy <- str_replace_all(survival_TCGA$chemotherapy, c("NO" = "No", "YES" = "Yes"))


survival_TCGA$radiation <- str_replace_all(survival_TCGA$radiation, c("NO" = "No", "YES" = "Yes"))
survival_TCGA$radiation[survival_TCGA$radiation == 'NA'] <- NA
survival_TCGA$radiation[survival_TCGA$radiation == '[Not Available]'] <- NA
survival_TCGA$radiation[survival_TCGA$radiation == '[Unknown]'] <- NA
survival_TCGA$radiation[survival_TCGA$radiation == '[Discrepancy]'] <- NA

survival_TCGA$stage <- str_replace_all(survival_TCGA$stage, c("Unknown" = "NA", "Unkown" = "NA"))
survival_TCGA$stage[survival_TCGA$stage == 'NA'] <- NA

write.csv(survival_TCGA, "survival_TCGA.csv")
```



