---
title: "nanostring subtype clean feb 16"
author: "Daniel Skubleny"
date: "16/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#NOTES
```{r}
Libraries <- c('matrixStats', 'ruv', 'NanoStringNorm', 'data.table','NormqPCR',
               'ComplexHeatmap','dplyr', 'plotrix', 'tuple', 'scales', 'ggplot2')
lapply(Libraries, require, character.only = TRUE)
rm(Libraries)

```
#FSQN fxn
```{r}
library(preprocessCore)
quantileNormalizeByFeature <- function(matrix_to_normalize,
                                       target_distribution_matrix){

    if (ncol(matrix_to_normalize) != ncol(target_distribution_matrix)){
        cat("ERROR: Data matrices are not compatible - column lengths differ!")
    }
    else{

        data.qn <- matrix(0, nrow = nrow(matrix_to_normalize),
                          ncol = ncol(matrix_to_normalize))

        for (i in 1:ncol(matrix_to_normalize)){
            feature.to.normalize <- matrix_to_normalize[,i]
            target.feature.dist <- target_distribution_matrix[,i]
            result <- normalize.quantiles.use.target(
                x = as.matrix(feature.to.normalize),
                target = target.feature.dist,
                copy = TRUE)
            data.qn[,i] <- result
        }
        rownames(data.qn) = rownames(matrix_to_normalize)
        colnames(data.qn) = colnames(matrix_to_normalize)
        return(data.qn)
    }
}
```
#Import data
```{r}
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/tcganormalizer.csv'
tcganormalizer <-read.csv(urlfile,row.names = 1)

urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/log_ACRG_cancer.csv'
log_ACRG_cancer <-read.csv(urlfile,row.names = 1)

urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/TCGAfinalgenes.csv'
TCGAfinalgenes <-read.csv(urlfile)
TCGAfinalgenes = TCGAfinalgenes[,2]

urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/rntop50.csv'
rntop50 <-read.csv(urlfile)
rntop50 = rntop50[,2]

```
#////////FFPE - gene specific normalization//////////
#TCGA RUVIII Normalization cancers with tcga only genes
```{r}
#***** Reading Nanostring gene expression raw data
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/run1-7.txt'
Nano_ExpressionMatrix <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)

#***** Reading sample and clinical information
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/nanostring_samples_final.txt'
Nano_SampleInfo <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)
Nano_SampleInfo = Nano_SampleInfo[c(1:84),]

dim(Nano_SampleInfo) # 24 12
table(Nano_SampleInfo$Tissues)


#Exclude poor samples
exclude = Nano_SampleInfo$exclude=="TRUE" 
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$exclude=="TRUE"),] 
Nano_SampleInfo = dplyr::select(Nano_SampleInfo, -"exclusion_reason")


Nano_RawCounts = dplyr::filter(Nano_ExpressionMatrix, subtype=="TCGA" | subtype=="Negative" | subtype=="Positive"| subtype=="Housekeeping")

#***** Expression matrix
Nano_RawCounts <- as.matrix(Nano_RawCounts[ , 5:ncol(Nano_RawCounts)])
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]



#Exclude organoids OR FFPE OR Cancer OR normal
exclude = Nano_SampleInfo$sample_type=="organoid"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$sample_type=="organoid"),] 

exclude = Nano_SampleInfo$Tissues=="normal"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$Tissues=="normal"),] 

row.names(Nano_RawCounts) <- Nano_ExpressionMatrix[Nano_ExpressionMatrix$subtype=="TCGA" | Nano_ExpressionMatrix$subtype=="Negative" |Nano_ExpressionMatrix$subtype=="Positive" |Nano_ExpressionMatrix$subtype=="Housekeeping" ,]$Probe.Name
Nano_SampleInfo$SampleNames <- colnames(Nano_RawCounts)


##################################################################################################################################
##################################################################  Exploratory  data analysis – raw counts #####################
#***** Colors for each cartridges
Color_Batches <- c('purple','orange','darkred','blue','chartreuse',
                   'darkgoldenrod4','tan2','darkgreen','red3','darkmagenta',
                   'deeppink','violet','navy','red','dodgerblue')

#***** box plot of raw data - Endogenous genes only

svg(filename="tcga_ffpe_unormalized.svg", width=8, height=5)

RawCounts_log <- log2(Nano_RawCounts[1:78 , ]+1) # Excluding 7 housekeeping genes and Nanostring spike-ins
par(mar = c(6.5,6.5,2.3,0), mgp = c(3.7 , 1 , 0))
boxplot(RawCounts_log, las = 1, cex.axis = 2, ylab = '' , xlab = '', cex.lab = 4,
        xaxt = 'n', yaxt = 'n', main = 'Unnormalized counts', cex.main = 3.5,
        outline = FALSE, names = FALSE, frame = FALSE,
        whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$Cartridges)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)] , col='gray87')
box(lwd = 7, bty = 'l')
axis(1, cex.axis=1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 4, mgp = c(3.5,1.6,0))
axis(2, at = c(0, seq(3,15,3)), mgp = c(3.5,.9,0), lwd.ticks = 4, las = 1, cex.axis=3)
mtext(expression(paste('Samples', '(', 'n'[samples], '=', '162', ')')), 1, line = 4.5, cex = 2.5)
mtext(expression(paste(Log[2],' (raw counts)')), 2, line = 3.5, cex = 2.7)
dev.off()

#***** RLE plot - Figure 1 A - Unormalized
par(mar = c(6.5,6.5,2.3,0))
boxplot(RawCounts_log - rowMedians(RawCounts_log),
        main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('Unnormalized counts', line = -2, cex.main = 3.5)
Median_RawData <- apply(RawCounts_log - rowMedians(RawCounts_log), 2, median)
points(c(1:ncol(RawCounts_log)), Median_RawData, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(2, mgp = c(3.5, .9 ,0), lwd.ticks=6, las=1, cex.axis=3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)
par(lwd = 3)
legend(160, 4.1, legend = c(1,2,3,'.','.','.', 13,14,15),
       col = c(Color_Batches[1:3], rep('white', 3), Color_Batches[13:15]),
       pch = 19, bty = 'n', cex = 1.4)
text(x = 162, y = 4.2 ,labels  = 'Cartridges', cex = 1.5)
rm(Median_RawData)


#####LONG 
counts = RawCounts_log - rowMedians(RawCounts_log)
counts = as.data.frame(t(counts))
counts$ID <- seq.int(nrow(counts))
counts$batchid = Nano_SampleInfo$cartridge

counts_long <- tidyr::gather(counts, gene, measurement, ABCB6:POS_F, factor_key=TRUE)
counts_long$ID = as.factor(counts_long$ID)
counts_long$batchid = as.factor(counts_long$batchid)

unnormalized_counts_tcga = ggplot(counts_long, aes(x=ID, y=measurement, fill=batchid)) + 
      geom_boxplot(notch=TRUE, outlier.shape=NA) +
      geom_hline(yintercept=0, size =1.5, alpha=0.7) +
      ggtitle("Unnormalized Counts TCGA Nanostring Genes") +
      xlab("Sample") + 
  ylab("Relative Log2 Expression") +
  ylim(-6,6) +
  theme_classic()  + 
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(colour="black",size = 13)) + 
  theme(plot.title = element_text(face="plain", colour="black", size=13,hjust = 0)) +
  theme(axis.title.x = element_text(colour="black", size =13)) +
  theme(axis.title.y = element_text(colour="black", size=13)) +
  theme(legend.position = "none")

ggsave("unnormalized_counts_tcga.svg", unnormalized_counts_tcga, width=6, height=3)

#***** Average plot
### Average of Nanostring positive spike-ins controls
Mean_NegativeControlProbes <- apply(Nano_RawCounts[65:72, ], 2, mean)
### Average of Nanostring positive spike-ins controls
Mean_PositiveControlProbes <- apply(Nano_RawCounts[73:78, ], 2, mean)
### Average of housekeeping genes
Mean_HousekeepingGenes <- apply(Nano_RawCounts[58:64, ], 2, mean)
### Library size
LibrarySize <- colSums(Nano_RawCounts [ 1:78, ])

#### Average plots -  Supplementary Figure 2
par(mar = c(6,7,0,0))
plot(log2(LibrarySize), ylim = c(0,22), bty = 'l', typ = 'n', ylab = '', xlab = '', xaxt = 'n', yaxt = 'n')
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1.4,0))
axis(2, cex.axis = 1, cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1,0), las = 1)
mtext(expression(paste(Log [2], ' (raw counts)')), 2, line = 3.5, cex = 3)
mtext(expression(paste('Samples', ' (', 'n'[samples], '=', '21', ')')), 1, line = 4.5, cex = 2.5)
X <- c(0,6,18,30,42,53,65,77,89,101,113,125,137,143,155,167)
GradiantColors <- paste0('gray', seq(90,20, by = -5))
for(i in 1:15) rect(X[i],-5, X[i+1], 22, col = GradiantColors[i], lty = 0 )
points(log2(LibrarySize), col = alpha('darkgoldenrod1', .8), pch = 15, cex = 1.8, lwd = 1.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(LibrarySize), df = 5), col = 'darkgoldenrod1', lwd = 4)
points(log2(Mean_HousekeepingGenes) + 3, cex = 2, col = alpha('red', .6), pch = 19)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_HousekeepingGenes) + 3, df = 5), col = 'red', lwd = 4)
points(log2(Mean_PositiveControlProbes) - 1, col = alpha('cyan2', .8), pch = 18, cex = 2.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_PositiveControlProbes) - 1, df = 5), col = 'cyan1', lwd = 4)
points(log2(Mean_NegativeControlProbes), col = alpha('green2', .6), pch = 17, cex = 1.8)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_NegativeControlProbes), df = 5), col = 'green2', lwd = 4)
box(lwd = 5, bty = 'l')
rm(X, GradiantColors, Mean_NegativeControlProbes,
   Mean_PositiveControlProbes, Mean_HousekeepingGenes,
   LibrarySize)


#***** Log ratio between all pairs of duplicated samples
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) 

LogRatio_TechRep_RawCounts <- vector()
for(i in 1:7){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[i]
  RepData <- RawCounts_log [ , index]
  LogRatio <- as.data.frame(RepData[ , 1] - RepData[ , 2] )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep( i , 78)
  LogRatio_TechRep_RawCounts <- rbind(LogRatio_TechRep_RawCounts , LogRatio)
  rm(i, index, RepData, LogRatio)
}
nrow(LogRatio_TechRep_RawCounts)/78 # 17
LogRatio_TechRep_RawCounts$Datasets <- 'Unnormalized'




##################################################################################################################################
############################################### RUV-III normalization - using technical replicates and control genes #############

#***** Creating replicate matrix
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133

### Making sure that every row has got only one number
par(mfrow = c(2,1))
barplot(colSums(ReplicateMatrix))
barplot(rowSums(ReplicateMatrix))
par(mfrow = c(1,1))


#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:57, ] + 1))
RUVcorrected <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:57))
RUVcorrected <- t(RUVcorrected)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 7)
RUVcorrected <- t(RUVcorrected)
dim(RUVcorrected)
# We tried different numbers of k based on our positive controls####
all(colnames(RUVcorrected) == Nano_SampleInfo$SampleNames) ## TRUE


#***** RLE plots - Figure 1 A, RUV-III normalization
par(mar = c(6.5,6.5,2.3,0))
boxplot(RUVcorrected - rowMedians(RUVcorrected), main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('RUV-III normalized', line = -2, cex.main = 3.5)
Median_RUV <- apply(RUVcorrected - rowMedians(RUVcorrected), 2, median)
points(c(1:ncol(RUVcorrected)), Median_RUV, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 6,  mgp = c(3.5,1.6,0))
axis(2, mgp = c(3.5,.9,0), lwd.ticks = 6, las = 1, cex.axis = 3)
mtext(expression(paste('Samples','(', 'n'[samples], '=', '162', ')')),1 ,line = 5, cex = 3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)

#####ggplot long

#####LONG 
counts = RUVcorrected - rowMedians(RUVcorrected)
counts = as.data.frame(t(counts))
counts$ID <- seq.int(nrow(counts))
counts$batchid = Nano_SampleInfo$cartridge

counts_long <- tidyr::gather(counts, gene, measurement, ABCB6:YBEY, factor_key=TRUE)
counts_long$ID = as.factor(counts_long$ID)
counts_long$batchid = as.factor(counts_long$batchid)

normalized_counts_tcga = ggplot(counts_long, aes(x=ID, y=measurement, fill=batchid)) + 
      geom_boxplot(notch=TRUE, outlier.shape=NA) +
      geom_hline(yintercept=0, size =1.5, alpha=0.7) +
      ggtitle("RUV-III Normalized Counts TCGA Nanostring Genes") +
      xlab("Sample") + 
  ylab("Relative Log2 Expression") +
  ylim(-6,6) +
  theme_classic()  + 
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(colour="black",size = 13)) + 
  theme(plot.title = element_text(face="plain", colour="black", size=13,hjust = 0)) +
  theme(axis.title.x = element_text(colour="black", size =13)) +
  theme(axis.title.y = element_text(colour="black", size=13)) +
  theme(legend.position = "none")

ggsave("normalized_counts_tcga.svg", normalized_counts_tcga, width=6, height=3)

#######

#***** Correlation between JAK2 and CDKN2A in cancer samples
RUVIII_CancerData <- RUVcorrected[ , Nano_SampleInfo$Tissues=="cancer"]
dim(RUVIII_CancerData) ## 587 150
BioCo_RUV <- cor.test(unlist(t(RUVIII_CancerData['CDKN2A' , ])) , unlist(t(RUVIII_CancerData[ 'JAK2' , ])), method = "spearman")[[4]]
par(mar = c(5,5,2,1))
plot (RUVIII_CancerData[ "CDKN2A", ], RUVIII_CancerData [ "JAK2" , ],
      las = 1, pch = 21, col = "cyan", bg = 'blue', lwd = 1.2,
      main = "RUV-III normalized", bty = "l", cex.main = 2, mgp = c(3.2,.8,0),
      cex.axis = 1.7, cex.lab = 1.5, cex = 2.5, lwd.ticks = 3, ylab = "" ,
      xlab = expression(paste(italic(RRM1) , " (", log[2] , " normalized counts" , ")")))
mtext(expression(paste(italic(ERCC1) , " (", log[2] , " normalized counts" , ")")), 2, line = 3, cex = 1.5)
title(paste('(r = ', round(BioCo_RUV, digits = 2), ')'), line = -.5, cex = 1.4)
box(lwd = 6, bty = "l")


#***** Log DIFFERENCE between technical duplicated - per the paper
### Assessing the perfromance of RUV-III using 'leave out one duplicate'
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) # 17
LogRatio_TechRep_RUVIII <- vector()
dataRUV <- t(log2(Nano_RawCounts[1:57, ] +1))

for(l in 1:length(DuplicatedSamples)){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[l]
  info <- Nano_SampleInfo
  info$Patient.barcodes[index] <- c('Rep1', 'Rep2')
  X <- length(info$Patient.barcodes)
  Y <- length(unique(info$Patient.barcodes))
  
  ReplicateMatrix <- matrix(0, nrow = X, ncol = Y)
  row.names(ReplicateMatrix) <- info$Patient.barcodes
  colnames(ReplicateMatrix) <- unique(info$Patient.barcodes)
  for(i in 1:Y){
    n <- colnames(ReplicateMatrix)[i]
    sa <- which(row.names(ReplicateMatrix)==n)
    for(j in 1:length(sa)){
      ReplicateMatrix [sa[j] , i] <- 1
    }
  }
  RUVcorrected_Data <- ruv::RUVIII(dataRUV , ReplicateMatrix , ctl = ControlGenes, k = 7)
  RUVcorrected_Data <- t(RUVcorrected_Data)
  index <- which(index)
  LogRatio <- as.data.frame( (RUVcorrected_Data[ , index[1]] ) - (RUVcorrected_Data[ , index[2]]) )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep(l , 57)
  LogRatio_TechRep_RUVIII <- rbind(LogRatio_TechRep_RUVIII , LogRatio)
  rm(i, index, info, X, Y, LogRatio)
  
}
nrow(LogRatio_TechRep_RUVIII)/57
LogRatio_TechRep_RUVIII$Datasets <- 'RUV-III normalized'


#***** Technical Replicate Agreement plot for unnormalized, Nanostring Normalization and RUV-III (leave out one technical replicate)
### Figure 1 B
TRAallNormalizations <- rbind(LogRatio_TechRep_RawCounts, LogRatio_TechRep_RUVIII)
TRAallNormalizations$Replicates <- as.factor(TRAallNormalizations$Replicates)
TRAallNormalizations$Datasets <- as.factor(TRAallNormalizations$Datasets)
TRAallNormalizations$Datasets  <- factor(TRAallNormalizations$Datasets , levels = c('Unnormalized','RUV-III normalized'))
ggplot(data = TRAallNormalizations) +
  geom_boxplot(aes(y = LogRatio, x = Replicates, fill = Datasets, color=Datasets), outlier.size = .5,
               position = position_dodge(width = .7),
               width = 1, alpha = 0.8, lwd = .7) +
  ylab('Log ratio')+ylim(c(-10,10)) +
  scale_color_manual(values = c('lightblue', 'royalblue', 'navy')) +
  scale_fill_manual(values = c('lightblue', 'royalblue', 'navy')) +
  theme_classic() +
  geom_hline(yintercept = 0, lty = 2, lwd = .6, col = 'red')+
  theme(axis.title = element_text(size = 25),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.line = element_line(size = 1.5),
        legend.title = element_text(size = 20, face = c('italic', 'bold')),
        legend.text = element_text(size = 20),
        legend.position = "top", legend.direction = "horizontal")

log_diff_tcga = ggplot(data = TRAallNormalizations) +
  geom_boxplot(aes(y = LogRatio, x = Replicates, fill = Datasets, color=Datasets), outlier.size = .5,
               position = position_dodge(width = .7),
               width = 1, alpha = 0.8, lwd = .7) +
  ylab('Log difference')+ylim(c(-10,10)) +
  scale_color_manual(values = c('lightblue', 'royalblue', 'navy')) +
  scale_fill_manual(values = c('lightblue', 'royalblue', 'navy')) +
  ggtitle("Technical replicate agreement plot") +
  theme_classic() +
  geom_hline(yintercept = 0, lty = 2, lwd = .6, col = 'red')+
  theme(axis.title = element_text(size = 13),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(size = 13),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 13),
        legend.position = c(0.5,0.92), legend.direction = "horizontal")
ggsave("log_diff_tcga.svg", log_diff_tcga, width=6, height=3)


############################################FINAL NORMALIZATION with 117 genes###################################################
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133
#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:57, ] +1))
RUVcorrected <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:57))
RUVcorrected <- t(RUVcorrected)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 7)
RUVcorrected <- t(RUVcorrected)
dim(RUVcorrected)
# We tried different numbers of k based on our positive controls
all(colnames(RUVcorrected) == Nano_SampleInfo$SampleNames) ## TRUE

tcga_ffpe_RUVcorrected= RUVcorrected
```

###TCGA RUVIII subtype
```{r}
log_nanostring_1 = RUVcorrected
```
```{r}
#Check if quantile normalization is required.
colramp = colorRampPalette(c(3,"white",2))(20)
plot(density(log_nanostring_1[,1]),col=colramp[1],lwd=1,ylim=c(0,.30), xlim=c(-20,20))
for(i in 2:9){lines(density(log_nanostring_1[,i]),lwd=1,col=colramp[i])}
#In the plot we can see that quantile normalization will aid in the data analysis
```
```{r}
housekeeping_genes = c("ACTB", "CTCF", "EIF4G", "HNRNPK", "RPL9", "SUMO3", "XRCC5")
normalizergenes = c(TCGAfinalgenes,housekeeping_genes)
```
```{r}
cancer_nanostring_1 <- subset(log_nanostring_1, rownames(log_nanostring_1) %in% as.matrix(TCGAfinalgenes))
cancer_nanostring_1 = t(cancer_nanostring_1)
```
```{r}
#FSQN the cancers

#TCGA FSQN to TCGA as reference.
set.seed(99)   
target = as.matrix(tcganormalizer)
test = as.matrix(cancer_nanostring_1)
classify_TCGA = quantileNormalizeByFeature(test, target)

colramp = colorRampPalette(c(3,"white",2))(20)
colramp2 = colorRampPalette(c(6,"white",4))(20)

svg(filename="prefsqn_tcga_nanostring_ffpe.svg", width=4.5, height=4)
par(mar = c(3.1, 4.1, 2.1, 2.1), mgp=c(2, 0.5, 0))
plot(density(t(target)[,1]), 
     main = "", 
     xlab = expression("Log"[2]*" Expression"), 
     xlim = c(-8,17),
     ylim = c(0,.32), 
     cex.lab=1.3,
     lwd=2, 
     col=colramp[1])
        for(i in 2:100){lines(density(t(target)[,i]),lwd=2,col=colramp[i])
        for(i in 2:48){lines(density(t(test)[,i]),lwd=2,col=colramp2[i])}}
    text(0, 0.27, labels="RUV-III")
    text(8.81, 0.31, labels="Target")
    title("Pre-FSQN", adj = 0, font.main= 1)
dev.off()

svg(filename="fsqn_tcga_nanostring_ffpe.svg", width=4.5, height=4)
par(mar = c(3.1, 4.1, 2.1, 2.1), mgp=c(2, 0.5, 0))
plot(density(t(target)[,1]), 
     main = "",
     xlab = expression("Log"[2]*" Expression"), 
     xlim = c(-8,17),
     ylim = c(0,.32), 
     cex.lab=1.3,
     lwd=2, 
     col=colramp[1])
        for(i in 2:100){lines(density(t(target)[,i]),lwd=2,col=colramp[i])
        for(i in 2:48){lines(density(t(classify_TCGA)[,i]),lwd=2,col=colramp2[i])}}
     text(8.81, 0.31, labels="Target/RUV-III")
     title("Post-FSQN", adj = 0, font.main= 1)
dev.off()

```
```{r}
#Reduce to final genes

classify_TCGA <- classify_TCGA[, TCGAfinalgenes]
```
```{r}
#Classify the cancers according to TCGA 

predict.classify_TCGA = predict(TCGA.finalmodel,classify_TCGA)
predict.classify_TCGA_prob = predict(TCGA.finalmodel,classify_TCGA, type = "prob")
TCGA_ffpe = predict.classify_TCGA_prob 

table(predict.classify_TCGA)

TCGA_ffpe = tibble::rownames_to_column(TCGA_ffpe, "sample_id")


TCGA_ffpe_names = Nano_SampleInfo
TCGA_ffpe_names = dplyr::select(TCGA_ffpe_names, c("Patient.barcodes","SampleNames"))

TCGA_ffpe = merge(TCGA_ffpe, TCGA_ffpe_names, by.x="sample_id", by.y="SampleNames")
TCGA_ffpe = TCGA_ffpe[,-1]
colnames(TCGA_ffpe)[which(names(TCGA_ffpe) == "Patient.barcodes")] <- "sample_id"



TCGA_ffpe %>% group_by(sample_id) %>% summarise_all(mean) %>% data.frame() -> TCGA_ffpe

TCGA_ffpe[,c(2:6)] = TCGA_ffpe[,c(2:5)] %>% mutate('TCGA_subtype'=names(.)[apply(., 1, which.max)])
```

#TME RUVIII Normalization cancers with TME only genes
```{r}
#***** Reading Nanostring gene expression raw data
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/run1-7.txt'
Nano_ExpressionMatrix <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)

#***** Reading sample and clinical information
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/nanostring_samples_final.txt'
Nano_SampleInfo <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)
Nano_SampleInfo = Nano_SampleInfo[c(1:84),]


dim(Nano_SampleInfo) # 24 12
table(Nano_SampleInfo$Tissues)


#Exclude poor samples
exclude = Nano_SampleInfo$exclude=="TRUE" 
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$exclude=="TRUE"),] 
Nano_SampleInfo = dplyr::select(Nano_SampleInfo, -"exclusion_reason")


Nano_RawCounts = dplyr::filter(Nano_ExpressionMatrix, subtype=="TME" | subtype=="Negative" | subtype=="Positive"| subtype=="Housekeeping")

#***** Expression matrix
Nano_RawCounts <- as.matrix(Nano_RawCounts[ , 5:ncol(Nano_RawCounts)])
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]



#Exclude organoids OR FFPE OR Cancer OR normal
exclude = Nano_SampleInfo$sample_type=="organoid"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$sample_type=="organoid"),] 

exclude = Nano_SampleInfo$Tissues=="normal"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$Tissues=="normal"),] 

row.names(Nano_RawCounts) <- Nano_ExpressionMatrix[Nano_ExpressionMatrix$subtype=="TME" | Nano_ExpressionMatrix$subtype=="Negative" |Nano_ExpressionMatrix$subtype=="Positive" |Nano_ExpressionMatrix$subtype=="Housekeeping" ,]$Probe.Name
Nano_SampleInfo$SampleNames <- colnames(Nano_RawCounts)


##################################################################################################################################
##################################################################  Exploratory  data analysis – raw counts #####################
#***** Colors for each cartridges
Color_Batches <- c('purple','orange','darkred','blue','chartreuse',
                   'darkgoldenrod4','tan2','darkgreen','red3','darkmagenta',
                   'deeppink','violet','navy','red','dodgerblue')

#***** box plot of raw data - Endogenous genes only
RawCounts_log <- log2(Nano_RawCounts[1:71 , ]+1) # Excluding 7 housekeeping genes and Nanostring spike-ins
par(mar = c(6.5,6.5,2.3,0), mgp = c(3.7 , 1 , 0))
boxplot(RawCounts_log, las = 1, cex.axis = 2, ylab = '' , xlab = '', cex.lab = 4,
        xaxt = 'n', yaxt = 'n', main = 'Unnormalized counts', cex.main = 3.5,
        outline = FALSE, names = FALSE, frame = FALSE,
        whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$Cartridges)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)] , col='gray87')
box(lwd = 7, bty = 'l')
axis(1, cex.axis=1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 4, mgp = c(3.5,1.6,0))
axis(2, at = c(0, seq(3,15,3)), mgp = c(3.5,.9,0), lwd.ticks = 4, las = 1, cex.axis=3)
mtext(expression(paste('Samples', '(', 'n'[samples], '=', '162', ')')), 1, line = 4.5, cex = 2.5)
mtext(expression(paste(Log[2],' (raw counts)')), 2, line = 3.5, cex = 2.7)


#***** RLE plot - Figure 1 A - Unormalized
par(mar = c(6.5,6.5,2.3,0))
boxplot(RawCounts_log - rowMedians(RawCounts_log),
        main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('Unnormalized counts', line = -2, cex.main = 3.5)
Median_RawData <- apply(RawCounts_log - rowMedians(RawCounts_log), 2, median)
points(c(1:ncol(RawCounts_log)), Median_RawData, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(2, mgp = c(3.5, .9 ,0), lwd.ticks=6, las=1, cex.axis=3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)
par(lwd = 3)
legend(160, 4.1, legend = c(1,2,3,'.','.','.', 13,14,15),
       col = c(Color_Batches[1:3], rep('white', 3), Color_Batches[13:15]),
       pch = 19, bty = 'n', cex = 1.4)
text(x = 162, y = 4.2 ,labels  = 'Cartridges', cex = 1.5)
rm(Median_RawData)


#***** Average plot
### Average of Nanostring positive spike-ins controls
Mean_NegativeControlProbes <- apply(Nano_RawCounts[58:65, ], 2, mean)
### Average of Nanostring positive spike-ins controls
Mean_PositiveControlProbes <- apply(Nano_RawCounts[66:71, ], 2, mean)
### Average of housekeeping genes
Mean_HousekeepingGenes <- apply(Nano_RawCounts[51:57, ], 2, mean)
### Library size
LibrarySize <- colSums(Nano_RawCounts [ 1:71, ])

#### Average plots -  Supplementary Figure 2
par(mar = c(6,7,0,0))
plot(log2(LibrarySize), ylim = c(0,22), bty = 'l', typ = 'n', ylab = '', xlab = '', xaxt = 'n', yaxt = 'n')
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1.4,0))
axis(2, cex.axis = 1, cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1,0), las = 1)
mtext(expression(paste(Log [2], ' (raw counts)')), 2, line = 3.5, cex = 3)
mtext(expression(paste('Samples', ' (', 'n'[samples], '=', '21', ')')), 1, line = 4.5, cex = 2.5)
X <- c(0,6,18,30,42,53,65,77,89,101,113,125,137,143,155,167)
GradiantColors <- paste0('gray', seq(90,20, by = -5))
for(i in 1:15) rect(X[i],-5, X[i+1], 22, col = GradiantColors[i], lty = 0 )
points(log2(LibrarySize), col = alpha('darkgoldenrod1', .8), pch = 15, cex = 1.8, lwd = 1.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(LibrarySize), df = 5), col = 'darkgoldenrod1', lwd = 4)
points(log2(Mean_HousekeepingGenes) + 3, cex = 2, col = alpha('red', .6), pch = 19)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_HousekeepingGenes) + 3, df = 5), col = 'red', lwd = 4)
points(log2(Mean_PositiveControlProbes) - 1, col = alpha('cyan2', .8), pch = 18, cex = 2.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_PositiveControlProbes) - 1, df = 5), col = 'cyan1', lwd = 4)
points(log2(Mean_NegativeControlProbes), col = alpha('green2', .6), pch = 17, cex = 1.8)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_NegativeControlProbes), df = 5), col = 'green2', lwd = 4)
box(lwd = 5, bty = 'l')
rm(X, GradiantColors, Mean_NegativeControlProbes,
   Mean_PositiveControlProbes, Mean_HousekeepingGenes,
   LibrarySize)


#***** Log ratio between all pairs of duplicated samples
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) 

LogRatio_TechRep_RawCounts <- vector()
for(i in 1:1){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[i]
  RepData <- RawCounts_log [ , index]
  LogRatio <- as.data.frame(RepData[ , 1] - RepData[ , 2] )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep( i , 71)
  LogRatio_TechRep_RawCounts <- rbind(LogRatio_TechRep_RawCounts , LogRatio)
  rm(i, index, RepData, LogRatio)
}
nrow(LogRatio_TechRep_RawCounts)/71 # 17
LogRatio_TechRep_RawCounts$Datasets <- 'Unnormalized'




##################################################################################################################################
############################################### RUV-III normalization - using technical replicates and control genes #############

#***** Creating replicate matrix
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133

### Making sure that every row has got only one number
par(mfrow = c(2,1))
barplot(colSums(ReplicateMatrix))
barplot(rowSums(ReplicateMatrix))
par(mfrow = c(1,1))


#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:50, ] + 1))
RUVcorrected <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:50))
RUVcorrected <- t(RUVcorrected)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 9) #NEEDED TO CHANGE TO 2
RUVcorrected <- t(RUVcorrected)
dim(RUVcorrected)
# We tried different numbers of k based on our positive controls####
all(colnames(RUVcorrected) == Nano_SampleInfo$SampleNames) ## TRUE


#***** RLE plots - Figure 1 A, RUV-III normalization
par(mar = c(6.5,6.5,2.3,0))
boxplot(RUVcorrected - rowMedians(RUVcorrected), main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('RUV-III normalized', line = -2, cex.main = 3.5)
Median_RUV <- apply(RUVcorrected - rowMedians(RUVcorrected), 2, median)
points(c(1:ncol(RUVcorrected)), Median_RUV, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 6,  mgp = c(3.5,1.6,0))
axis(2, mgp = c(3.5,.9,0), lwd.ticks = 6, las = 1, cex.axis = 3)
mtext(expression(paste('Samples','(', 'n'[samples], '=', '162', ')')),1 ,line = 5, cex = 3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)


#***** Correlation between ERCC1 and RRM1 in cancer samples
RUVIII_CancerData <- RUVcorrected[ , Nano_SampleInfo$Tissues=="cancer"]
dim(RUVIII_CancerData) ## 587 150
BioCo_RUV <- cor.test(unlist(t(RUVIII_CancerData['SMAD9' , ])) , unlist(t(RUVIII_CancerData[ 'WARS1' , ])), method = "spearman")[[4]]
par(mar = c(5,5,2,1))
plot (RUVIII_CancerData[ "SMAD9", ], RUVIII_CancerData [ "WARS1" , ],
      las = 1, pch = 21, col = "cyan", bg = 'blue', lwd = 1.2,
      main = "RUV-III normalized", bty = "l", cex.main = 2, mgp = c(3.2,.8,0),
      cex.axis = 1.7, cex.lab = 1.5, cex = 2.5, lwd.ticks = 3, ylab = "" ,
      xlab = expression(paste(italic(RRM1) , " (", log[2] , " normalized counts" , ")")))
mtext(expression(paste(italic(ERCC1) , " (", log[2] , " normalized counts" , ")")), 2, line = 3, cex = 1.5)
title(paste('(r = ', round(BioCo_RUV, digits = 2), ')'), line = -.5, cex = 1.4)
box(lwd = 6, bty = "l")


#***** Log DIFFERENCE between technical duplicated - per the paper
### Assessing the perfromance of RUV-III using 'leave out one duplicate'
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) # 17
LogRatio_TechRep_RUVIII <- vector()
dataRUV <- t(log2(Nano_RawCounts[1:51, ] +1))

for(l in 1:length(DuplicatedSamples)){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[l]
  info <- Nano_SampleInfo
  info$Patient.barcodes[index] <- c('Rep1', 'Rep2')
  X <- length(info$Patient.barcodes)
  Y <- length(unique(info$Patient.barcodes))
  
  ReplicateMatrix <- matrix(0, nrow = X, ncol = Y)
  row.names(ReplicateMatrix) <- info$Patient.barcodes
  colnames(ReplicateMatrix) <- unique(info$Patient.barcodes)
  for(i in 1:Y){
    n <- colnames(ReplicateMatrix)[i]
    sa <- which(row.names(ReplicateMatrix)==n)
    for(j in 1:length(sa)){
      ReplicateMatrix [sa[j] , i] <- 1
    }
  }
  RUVcorrected_Data <- ruv::RUVIII(dataRUV , ReplicateMatrix , ctl = ControlGenes, k = 9)
  RUVcorrected_Data <- t(RUVcorrected_Data)
  index <- which(index)
  LogRatio <- as.data.frame( (RUVcorrected_Data[ , index[1]] ) - (RUVcorrected_Data[ , index[2]]) )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep(l , 51)
  LogRatio_TechRep_RUVIII <- rbind(LogRatio_TechRep_RUVIII , LogRatio)
  rm(i, index, info, X, Y, LogRatio)
  
}
nrow(LogRatio_TechRep_RUVIII)/51
LogRatio_TechRep_RUVIII$Datasets <- 'RUV-III normalized'


#***** Technical Replicate Agreement plot for unnormalized, Nanostring Normalization and RUV-III (leave out one technical replicate)
### Figure 1 B
TRAallNormalizations <- rbind(LogRatio_TechRep_RawCounts, LogRatio_TechRep_RUVIII)
TRAallNormalizations$Replicates <- as.factor(TRAallNormalizations$Replicates)
TRAallNormalizations$Datasets <- as.factor(TRAallNormalizations$Datasets)
TRAallNormalizations$Datasets  <- factor(TRAallNormalizations$Datasets , levels = c('Unnormalized','RUV-III normalized'))
ggplot(data = TRAallNormalizations) +
  geom_boxplot(aes(y = LogRatio, x = Replicates, fill = Datasets, color=Datasets), outlier.size = .5,
               position = position_dodge(width = .7),
               width = 1, alpha = 0.8, lwd = .7) +
  ylab('Log ratio')+ylim(c(-10,10)) +
  scale_color_manual(values = c('lightblue', 'royalblue', 'navy')) +
  scale_fill_manual(values = c('lightblue', 'royalblue', 'navy')) +
  theme_classic() +
  geom_hline(yintercept = 0, lty = 2, lwd = .6, col = 'red')+
  theme(axis.title = element_text(size = 25),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.line = element_line(size = 1.5),
        legend.title = element_text(size = 20, face = c('italic', 'bold')),
        legend.text = element_text(size = 20),
        legend.position = "top", legend.direction = "horizontal")


############################################FINAL NORMALIZATION with 117 genes###################################################
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133
#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:51, ] +1))
RUVcorrected <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:51))
RUVcorrected <- t(RUVcorrected)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 9)
RUVcorrected <- t(RUVcorrected)
dim(RUVcorrected)
# We tried different numbers of k based on our positive controls
all(colnames(RUVcorrected) == Nano_SampleInfo$SampleNames) ## TRUE

tme_ffpe_RUVcorrected= RUVcorrected

```
###TME RUVIII subtype
```{r}
log_nanostring_1 = RUVcorrected
```
```{r}
#Check if quantile normalization is required.
colramp = colorRampPalette(c(3,"white",2))(20)
plot(density(log_nanostring_1[,1]),col=colramp[1],lwd=1,ylim=c(0,.30), xlim=c(-20,20))
for(i in 2:9){lines(density(log_nanostring_1[,i]),lwd=1,col=colramp[i])}
#In the plot we can see that quantile normalization will aid in the data analysis
```

```{r}
housekeeping_genes = c("ACTB", "CTCF", "EIF4G", "HNRNPK", "RPL9", "SUMO3", "XRCC5")
normalizergenes = c(rntop50,housekeeping_genes)
```

```{r}
#Data sets - reduce to commongenes and transpose for FSQN
cancer_nanostring_1 <- subset(log_nanostring_1, rownames(log_nanostring_1) %in% as.matrix(rntop50))
cancer_nanostring_1 = t(cancer_nanostring_1)
```

```{r}
#FSQN the cancers

#TCGA FSQN to ACRG as reference due to predominate data derived from affymetrix platform and that TME clusters were established ACRG.
set.seed(99)   
target = as.matrix(log_ACRG_cancer)
test = as.matrix(cancer_nanostring_1)
classify_TME = quantileNormalizeByFeature(test, target)

colramp = colorRampPalette(c(3,"white",2))(20)
colramp2 = colorRampPalette(c(4,"white",5))(20)
plot(density(log_nanostring_1[,1]),col=colramp[1],lwd=1,ylim=c(0,.30), xlim=c(-20,20))
for(i in 2:9){lines(density(log_nanostring_1[,i]),lwd=1,col=colramp[i])
  for(i in 2:9){lines(density(t(classify_TME)[,i]),lwd=1,col=colramp2[i])}
}
```
```{r}
#Reduce to final genes

classify_TME <- classify_TME[, rntop50]
```
```{r}
#Classify the cancers according to TCGA 

predict.classify_TME = predict(tme.final,classify_TME)
predict.classify_TME_prob = predict(tme.final,classify_TME, type = "prob")

table(predict.classify_TME)
```
```{r}
#Extract calibrated probabilities 

predict.classify_TME_cal = predict(tme.final_calibration,predict.classify_TME_prob)
predict.classify_TME_prob_cal = predict(tme.final_calibration,predict.classify_TME_prob, type = "prob")
colnames(predict.classify_TME_prob_cal) = c("High_cal", "Low_cal")

TME_cal = as.data.frame(row.names(classify_TME))
TME_cal$TME_subtype_cal = predict.classify_TME_cal
colnames(TME_cal)[which(names(TME_cal) == "row.names(classify_TME)")] <- "sample_id"

TME_prob_cal = as.data.frame(row.names(classify_TME))
TME_prob_cal$High_cal = predict.classify_TME_prob_cal$High_cal
TME_prob_cal$Low_cal = predict.classify_TME_prob_cal$Low_cal
colnames(TME_prob_cal)[which(names(TME_prob_cal) == "row.names(classify_TME)")] <- "sample_id"

TME_ffpe = TME_prob_cal

TME_ffpe_names = Nano_SampleInfo
TME_ffpe_names = dplyr::select(TME_ffpe_names, c("Patient.barcodes","SampleNames"))

TME_ffpe = merge(TME_ffpe, TME_ffpe_names, by.x="sample_id", by.y="SampleNames")
TME_ffpe = TME_ffpe[,-1]
colnames(TME_ffpe)[which(names(TME_ffpe) == "Patient.barcodes")] <- "sample_id"





TME_ffpe %>% group_by(sample_id) %>% summarise_all(mean) %>% data.frame() -> TME_ffpe

TME_ffpe[,c(2:4)] = TME_ffpe[,c(2:3)] %>% mutate('TME_subtype'=names(.)[apply(., 1, which.max)])

TCGA_ffpe[,c(2:6)] = TCGA_ffpe[,c(2:5)] %>% mutate('TCGA_subtype'=names(.)[apply(., 1, which.max)])
```

```{r}
#Combine FFPE TCGA and TME
ffpe_nanostring = merge(TCGA_ffpe,TME_ffpe, by="sample_id")

ffpe_nanostring$tissue = "ffpe"

```


#////////Organoid - gene specific normalization//////////
#TCGA RUVIII Normalization cancers with tcga only genes
The optimal normalization normalizes FFPE and organoid separately. The Normals and Cancers are included together. 117 genes are used... the "housekeepers" are excluded. 
```{r}
#***** Reading Nanostring gene expression raw data
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/run1-7.txt'
Nano_ExpressionMatrix <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)

#***** Reading sample and clinical information
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/nanostring_samples_final.txt'
Nano_SampleInfo <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)
Nano_SampleInfo = Nano_SampleInfo[c(1:84),]


dim(Nano_SampleInfo) # 24 12
table(Nano_SampleInfo$Tissues)


#Exclude poor samples
exclude = Nano_SampleInfo$exclude=="TRUE" 
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$exclude=="TRUE"),] 
Nano_SampleInfo = dplyr::select(Nano_SampleInfo, -"exclusion_reason")


Nano_RawCounts = dplyr::filter(Nano_ExpressionMatrix, subtype=="TCGA" | subtype=="Negative" | subtype=="Positive"| subtype=="Housekeeping")

#***** Expression matrix
Nano_RawCounts <- as.matrix(Nano_RawCounts[ , 5:ncol(Nano_RawCounts)])
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]



#Exclude organoids OR FFPE OR Cancer OR normal
exclude = Nano_SampleInfo$sample_type=="FFPE"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$sample_type=="FFPE"),] 

exclude = Nano_SampleInfo$Tissues=="normal_organoid"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$Tissues=="normal_organoid"),] 

row.names(Nano_RawCounts) <- Nano_ExpressionMatrix[Nano_ExpressionMatrix$subtype=="TCGA" | Nano_ExpressionMatrix$subtype=="Negative" |Nano_ExpressionMatrix$subtype=="Positive" |Nano_ExpressionMatrix$subtype=="Housekeeping" ,]$Probe.Name
Nano_SampleInfo$SampleNames <- colnames(Nano_RawCounts)


##################################################################################################################################
##################################################################  Exploratory  data analysis – raw counts #####################
#***** Colors for each cartridges
Color_Batches <- c('purple','orange','darkred','blue','chartreuse',
                   'darkgoldenrod4','tan2','darkgreen','red3','darkmagenta',
                   'deeppink','violet','navy','red','dodgerblue')

#***** box plot of raw data - Endogenous genes only
RawCounts_log <- log2(Nano_RawCounts[1:78 , ]+1) # Excluding 7 housekeeping genes and Nanostring spike-ins
par(mar = c(6.5,6.5,2.3,0), mgp = c(3.7 , 1 , 0))
boxplot(RawCounts_log, las = 1, cex.axis = 2, ylab = '' , xlab = '', cex.lab = 4,
        xaxt = 'n', yaxt = 'n', main = 'Unnormalized counts', cex.main = 3.5,
        outline = FALSE, names = FALSE, frame = FALSE,
        whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$Cartridges)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)] , col='gray87')
box(lwd = 7, bty = 'l')
axis(1, cex.axis=1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 4, mgp = c(3.5,1.6,0))
axis(2, at = c(0, seq(3,15,3)), mgp = c(3.5,.9,0), lwd.ticks = 4, las = 1, cex.axis=3)
mtext(expression(paste('Samples', '(', 'n'[samples], '=', '162', ')')), 1, line = 4.5, cex = 2.5)
mtext(expression(paste(Log[2],' (raw counts)')), 2, line = 3.5, cex = 2.7)


#***** RLE plot - Figure 1 A - Unormalized
par(mar = c(6.5,6.5,2.3,0))
boxplot(RawCounts_log - rowMedians(RawCounts_log),
        main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('Unnormalized counts', line = -2, cex.main = 3.5)
Median_RawData <- apply(RawCounts_log - rowMedians(RawCounts_log), 2, median)
points(c(1:ncol(RawCounts_log)), Median_RawData, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(2, mgp = c(3.5, .9 ,0), lwd.ticks=6, las=1, cex.axis=3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)
par(lwd = 3)
legend(160, 4.1, legend = c(1,2,3,'.','.','.', 13,14,15),
       col = c(Color_Batches[1:3], rep('white', 3), Color_Batches[13:15]),
       pch = 19, bty = 'n', cex = 1.4)
text(x = 162, y = 4.2 ,labels  = 'Cartridges', cex = 1.5)
rm(Median_RawData)


#***** Average plot
### Average of Nanostring positive spike-ins controls
Mean_NegativeControlProbes <- apply(Nano_RawCounts[65:72, ], 2, mean)
### Average of Nanostring positive spike-ins controls
Mean_PositiveControlProbes <- apply(Nano_RawCounts[73:78, ], 2, mean)
### Average of housekeeping genes
Mean_HousekeepingGenes <- apply(Nano_RawCounts[58:64, ], 2, mean)
### Library size
LibrarySize <- colSums(Nano_RawCounts [ 1:78, ])

#### Average plots -  Supplementary Figure 2
par(mar = c(6,7,0,0))
plot(log2(LibrarySize), ylim = c(0,22), bty = 'l', typ = 'n', ylab = '', xlab = '', xaxt = 'n', yaxt = 'n')
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1.4,0))
axis(2, cex.axis = 1, cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1,0), las = 1)
mtext(expression(paste(Log [2], ' (raw counts)')), 2, line = 3.5, cex = 3)
mtext(expression(paste('Samples', ' (', 'n'[samples], '=', '21', ')')), 1, line = 4.5, cex = 2.5)
X <- c(0,6,18,30,42,53,65,77,89,101,113,125,137,143,155,167)
GradiantColors <- paste0('gray', seq(90,20, by = -5))
for(i in 1:15) rect(X[i],-5, X[i+1], 22, col = GradiantColors[i], lty = 0 )
points(log2(LibrarySize), col = alpha('darkgoldenrod1', .8), pch = 15, cex = 1.8, lwd = 1.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(LibrarySize), df = 5), col = 'darkgoldenrod1', lwd = 4)
points(log2(Mean_HousekeepingGenes) + 3, cex = 2, col = alpha('red', .6), pch = 19)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_HousekeepingGenes) + 3, df = 5), col = 'red', lwd = 4)
points(log2(Mean_PositiveControlProbes) - 1, col = alpha('cyan2', .8), pch = 18, cex = 2.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_PositiveControlProbes) - 1, df = 5), col = 'cyan1', lwd = 4)
points(log2(Mean_NegativeControlProbes), col = alpha('green2', .6), pch = 17, cex = 1.8)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_NegativeControlProbes), df = 5), col = 'green2', lwd = 4)
box(lwd = 5, bty = 'l')
rm(X, GradiantColors, Mean_NegativeControlProbes,
   Mean_PositiveControlProbes, Mean_HousekeepingGenes,
   LibrarySize)


#***** Log ratio between all pairs of duplicated samples
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) 

LogRatio_TechRep_RawCounts <- vector()
for(i in 1:1){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[i]
  RepData <- RawCounts_log [ , index]
  LogRatio <- as.data.frame(RepData[ , 1] - RepData[ , 2] )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep( i , 78)
  LogRatio_TechRep_RawCounts <- rbind(LogRatio_TechRep_RawCounts , LogRatio)
  rm(i, index, RepData, LogRatio)
}
nrow(LogRatio_TechRep_RawCounts)/78 # 17
LogRatio_TechRep_RawCounts$Datasets <- 'Unnormalized'




##################################################################################################################################
############################################### RUV-III normalization - using technical replicates and control genes #############

#***** Creating replicate matrix
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133

### Making sure that every row has got only one number
par(mfrow = c(2,1))
barplot(colSums(ReplicateMatrix))
barplot(rowSums(ReplicateMatrix))
par(mfrow = c(1,1))


#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:57, ] + 1))
RUVcorrected <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:57))
RUVcorrected <- t(RUVcorrected)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 2)
RUVcorrected <- t(RUVcorrected)
dim(RUVcorrected)
# We tried different numbers of k based on our positive controls####
all(colnames(RUVcorrected) == Nano_SampleInfo$SampleNames) ## TRUE


#***** RLE plots - Figure 1 A, RUV-III normalization
par(mar = c(6.5,6.5,2.3,0))
boxplot(RUVcorrected - rowMedians(RUVcorrected), main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('RUV-III normalized', line = -2, cex.main = 3.5)
Median_RUV <- apply(RUVcorrected - rowMedians(RUVcorrected), 2, median)
points(c(1:ncol(RUVcorrected)), Median_RUV, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 6,  mgp = c(3.5,1.6,0))
axis(2, mgp = c(3.5,.9,0), lwd.ticks = 6, las = 1, cex.axis = 3)
mtext(expression(paste('Samples','(', 'n'[samples], '=', '162', ')')),1 ,line = 5, cex = 3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)


#***** Correlation between ERCC1 and RRM1 in cancer samples
RUVIII_CancerData <- RUVcorrected[ , Nano_SampleInfo$Tissues=="cancer_organoid"]
dim(RUVIII_CancerData) ## 587 150
BioCo_RUV <- cor.test(unlist(t(RUVIII_CancerData['CDKN2A' , ])) , unlist(t(RUVIII_CancerData[ 'JAK2' , ])), method = "spearman")[[4]]
par(mar = c(5,5,2,1))
plot (RUVIII_CancerData[ "CDKN2A", ], RUVIII_CancerData [ "JAK2" , ],
      las = 1, pch = 21, col = "cyan", bg = 'blue', lwd = 1.2,
      main = "RUV-III normalized", bty = "l", cex.main = 2, mgp = c(3.2,.8,0),
      cex.axis = 1.7, cex.lab = 1.5, cex = 2.5, lwd.ticks = 3, ylab = "" ,
      xlab = expression(paste(italic(RRM1) , " (", log[2] , " normalized counts" , ")")))
mtext(expression(paste(italic(ERCC1) , " (", log[2] , " normalized counts" , ")")), 2, line = 3, cex = 1.5)
title(paste('(r = ', round(BioCo_RUV, digits = 2), ')'), line = -.5, cex = 1.4)
box(lwd = 6, bty = "l")


#***** Log DIFFERENCE between technical duplicated - per the paper
### Assessing the perfromance of RUV-III using 'leave out one duplicate'
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) # 17
LogRatio_TechRep_RUVIII <- vector()
dataRUV <- t(log2(Nano_RawCounts[1:57, ] +1))

for(l in 1:length(DuplicatedSamples)){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[l]
  info <- Nano_SampleInfo
  info$Patient.barcodes[index] <- c('Rep1', 'Rep2')
  X <- length(info$Patient.barcodes)
  Y <- length(unique(info$Patient.barcodes))
  
  ReplicateMatrix <- matrix(0, nrow = X, ncol = Y)
  row.names(ReplicateMatrix) <- info$Patient.barcodes
  colnames(ReplicateMatrix) <- unique(info$Patient.barcodes)
  for(i in 1:Y){
    n <- colnames(ReplicateMatrix)[i]
    sa <- which(row.names(ReplicateMatrix)==n)
    for(j in 1:length(sa)){
      ReplicateMatrix [sa[j] , i] <- 1
    }
  }
  RUVcorrected_Data <- ruv::RUVIII(dataRUV , ReplicateMatrix , ctl = ControlGenes, k = 2)
  RUVcorrected_Data <- t(RUVcorrected_Data)
  index <- which(index)
  LogRatio <- as.data.frame( (RUVcorrected_Data[ , index[1]] ) - (RUVcorrected_Data[ , index[2]]) )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep(l , 57)
  LogRatio_TechRep_RUVIII <- rbind(LogRatio_TechRep_RUVIII , LogRatio)
  rm(i, index, info, X, Y, LogRatio)
  
}
nrow(LogRatio_TechRep_RUVIII)/57
LogRatio_TechRep_RUVIII$Datasets <- 'RUV-III normalized'


#***** Technical Replicate Agreement plot for unnormalized, Nanostring Normalization and RUV-III (leave out one technical replicate)
### Figure 1 B
TRAallNormalizations <- rbind(LogRatio_TechRep_RawCounts, LogRatio_TechRep_RUVIII)
TRAallNormalizations$Replicates <- as.factor(TRAallNormalizations$Replicates)
TRAallNormalizations$Datasets <- as.factor(TRAallNormalizations$Datasets)
TRAallNormalizations$Datasets  <- factor(TRAallNormalizations$Datasets , levels = c('Unnormalized','RUV-III normalized'))
ggplot(data = TRAallNormalizations) +
  geom_boxplot(aes(y = LogRatio, x = Replicates, fill = Datasets, color=Datasets), outlier.size = .5,
               position = position_dodge(width = .7),
               width = 1, alpha = 0.8, lwd = .7) +
  ylab('Log ratio')+ylim(c(-10,10)) +
  scale_color_manual(values = c('lightblue', 'royalblue', 'navy')) +
  scale_fill_manual(values = c('lightblue', 'royalblue', 'navy')) +
  theme_classic() +
  geom_hline(yintercept = 0, lty = 2, lwd = .6, col = 'red')+
  theme(axis.title = element_text(size = 25),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.line = element_line(size = 1.5),
        legend.title = element_text(size = 20, face = c('italic', 'bold')),
        legend.text = element_text(size = 20),
        legend.position = "top", legend.direction = "horizontal")



############################################FINAL NORMALIZATION with 117 genes###################################################
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133
#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:57, ] +1))
RUVcorrected_organoid <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:57))
RUVcorrected_organoid <- t(RUVcorrected_organoid)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected_organoid, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected_organoid <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 2)
RUVcorrected_organoid <- t(RUVcorrected_organoid)
dim(RUVcorrected_organoid)
# We tried different numbers of k based on our positive controls
all(colnames(RUVcorrected_organoid) == Nano_SampleInfo$SampleNames) ## TRUE


```
###TCGA RUVIII subtype
```{r}
log_nanostring_1 = RUVcorrected_organoid
```
```{r}
#Check if quantile normalization is required.
colramp = colorRampPalette(c(3,"white",2))(20)
plot(density(log_nanostring_1[,1]),col=colramp[1],lwd=1,ylim=c(0,.30), xlim=c(-20,20))
for(i in 2:9){lines(density(log_nanostring_1[,i]),lwd=1,col=colramp[i])}
#In the plot we can see that quantile normalization will aid in the data analysis
```
```{r}
housekeeping_genes = c("ACTB", "CTCF", "EIF4G", "HNRNPK", "RPL9", "SUMO3", "XRCC5")
normalizergenes = c(TCGAfinalgenes,housekeeping_genes)
```
```{r}
cancer_nanostring_1 <- subset(log_nanostring_1, rownames(log_nanostring_1) %in% as.matrix(TCGAfinalgenes))
cancer_nanostring_1 = t(cancer_nanostring_1)
```
```{r}
#FSQN the cancers

#TCGA FSQN to TCGA as reference.
set.seed(99)   
target = as.matrix(tcganormalizer)
test = as.matrix(cancer_nanostring_1)
classify_TCGA = quantileNormalizeByFeature(test, target)
```
```{r}
#Reduce to final genes

classify_TCGA <- classify_TCGA[, TCGAfinalgenes]
```

```{r}
#Classify the cancers according to TCGA 

predict.classify_TCGA = predict(TCGA.finalmodel,classify_TCGA)
predict.classify_TCGA_prob = predict(TCGA.finalmodel,classify_TCGA, type = "prob")
TCGA_ffpe = predict.classify_TCGA_prob 

table(predict.classify_TCGA)

TCGA_ffpe = tibble::rownames_to_column(TCGA_ffpe, "sample_id")

TCGA_ffpe_names = Nano_SampleInfo
TCGA_ffpe_names = dplyr::select(TCGA_ffpe_names, c("Patient.barcodes","SampleNames"))

TCGA_ffpe = merge(TCGA_ffpe, TCGA_ffpe_names, by.x="sample_id", by.y="SampleNames")
TCGA_ffpe = TCGA_ffpe[,-1]
colnames(TCGA_ffpe)[which(names(TCGA_ffpe) == "Patient.barcodes")] <- "sample_id"



TCGA_ffpe %>% group_by(sample_id) %>% summarise_all(mean) %>% data.frame() -> TCGA_ffpe

TCGA_ffpe[,c(2:6)] = TCGA_ffpe[,c(2:5)] %>% mutate('TCGA_subtype'=names(.)[apply(., 1, which.max)])
```

#TME RUVIII Normalization cancers with tcga only genes
```{r}
#***** Reading Nanostring gene expression raw data
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/run1-7.txt'
Nano_ExpressionMatrix <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)

#***** Reading sample and clinical information
urlfile<-'https://raw.githubusercontent.com/skubleny/Integrated-Molecular-Classification-GC/main/Data/nanostring_samples_final.txt'
Nano_SampleInfo <-read.delim(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)
Nano_SampleInfo = Nano_SampleInfo[c(1:84),]


dim(Nano_SampleInfo) # 24 12
table(Nano_SampleInfo$Tissues)


#Exclude poor samples
exclude = Nano_SampleInfo$exclude=="TRUE" 
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$exclude=="TRUE"),] 
Nano_SampleInfo = dplyr::select(Nano_SampleInfo, -"exclusion_reason")


Nano_RawCounts = dplyr::filter(Nano_ExpressionMatrix, subtype=="TME" | subtype=="Negative" | subtype=="Positive"| subtype=="Housekeeping")

#***** Expression matrix
Nano_RawCounts <- as.matrix(Nano_RawCounts[ , 5:ncol(Nano_RawCounts)])
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]



#Exclude organoids OR FFPE OR Cancer OR normal
exclude = Nano_SampleInfo$sample_type=="FFPE"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$sample_type=="FFPE"),] 

exclude = Nano_SampleInfo$Tissues=="normal_organoid"
exclude = colnames(Nano_RawCounts[,exclude])
Nano_RawCounts = Nano_RawCounts[ , !(colnames(Nano_RawCounts) %in% exclude)]
Nano_SampleInfo = Nano_SampleInfo[!(Nano_SampleInfo$Tissues=="normal_organoid"),] 

row.names(Nano_RawCounts) <- Nano_ExpressionMatrix[Nano_ExpressionMatrix$subtype=="TME" | Nano_ExpressionMatrix$subtype=="Negative" |Nano_ExpressionMatrix$subtype=="Positive" |Nano_ExpressionMatrix$subtype=="Housekeeping" ,]$Probe.Name
Nano_SampleInfo$SampleNames <- colnames(Nano_RawCounts)


##################################################################################################################################
##################################################################  Exploratory  data analysis – raw counts #####################
#***** Colors for each cartridges
Color_Batches <- c('purple','orange','darkred','blue','chartreuse',
                   'darkgoldenrod4','tan2','darkgreen','red3','darkmagenta',
                   'deeppink','violet','navy','red','dodgerblue')

#***** box plot of raw data - Endogenous genes only
RawCounts_log <- log2(Nano_RawCounts[1:71 , ]+1) # Excluding 7 housekeeping genes and Nanostring spike-ins
par(mar = c(6.5,6.5,2.3,0), mgp = c(3.7 , 1 , 0))
boxplot(RawCounts_log, las = 1, cex.axis = 2, ylab = '' , xlab = '', cex.lab = 4,
        xaxt = 'n', yaxt = 'n', main = 'Unnormalized counts', cex.main = 3.5,
        outline = FALSE, names = FALSE, frame = FALSE,
        whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$Cartridges)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)] , col='gray87')
box(lwd = 7, bty = 'l')
axis(1, cex.axis=1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 4, mgp = c(3.5,1.6,0))
axis(2, at = c(0, seq(3,15,3)), mgp = c(3.5,.9,0), lwd.ticks = 4, las = 1, cex.axis=3)
mtext(expression(paste('Samples', '(', 'n'[samples], '=', '162', ')')), 1, line = 4.5, cex = 2.5)
mtext(expression(paste(Log[2],' (raw counts)')), 2, line = 3.5, cex = 2.7)


#***** RLE plot - Figure 1 A - Unormalized
par(mar = c(6.5,6.5,2.3,0))
boxplot(RawCounts_log - rowMedians(RawCounts_log),
        main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('Unnormalized counts', line = -2, cex.main = 3.5)
Median_RawData <- apply(RawCounts_log - rowMedians(RawCounts_log), 2, median)
points(c(1:ncol(RawCounts_log)), Median_RawData, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(2, mgp = c(3.5, .9 ,0), lwd.ticks=6, las=1, cex.axis=3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)
par(lwd = 3)
legend(160, 4.1, legend = c(1,2,3,'.','.','.', 13,14,15),
       col = c(Color_Batches[1:3], rep('white', 3), Color_Batches[13:15]),
       pch = 19, bty = 'n', cex = 1.4)
text(x = 162, y = 4.2 ,labels  = 'Cartridges', cex = 1.5)
rm(Median_RawData)


#***** Average plot
### Average of Nanostring positive spike-ins controls
Mean_NegativeControlProbes <- apply(Nano_RawCounts[58:65, ], 2, mean)
### Average of Nanostring positive spike-ins controls
Mean_PositiveControlProbes <- apply(Nano_RawCounts[66:71, ], 2, mean)
### Average of housekeeping genes
Mean_HousekeepingGenes <- apply(Nano_RawCounts[51:57, ], 2, mean)
### Library size
LibrarySize <- colSums(Nano_RawCounts [ 1:71, ])

#### Average plots -  Supplementary Figure 2
par(mar = c(6,7,0,0))
plot(log2(LibrarySize), ylim = c(0,22), bty = 'l', typ = 'n', ylab = '', xlab = '', xaxt = 'n', yaxt = 'n')
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1.4,0))
axis(2, cex.axis = 1, cex.axis = 2, lwd.ticks = 4, mgp = c(3.5,1,0), las = 1)
mtext(expression(paste(Log [2], ' (raw counts)')), 2, line = 3.5, cex = 3)
mtext(expression(paste('Samples', ' (', 'n'[samples], '=', '21', ')')), 1, line = 4.5, cex = 2.5)
X <- c(0,6,18,30,42,53,65,77,89,101,113,125,137,143,155,167)
GradiantColors <- paste0('gray', seq(90,20, by = -5))
for(i in 1:15) rect(X[i],-5, X[i+1], 22, col = GradiantColors[i], lty = 0 )
points(log2(LibrarySize), col = alpha('darkgoldenrod1', .8), pch = 15, cex = 1.8, lwd = 1.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(LibrarySize), df = 5), col = 'darkgoldenrod1', lwd = 4)
points(log2(Mean_HousekeepingGenes) + 3, cex = 2, col = alpha('red', .6), pch = 19)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_HousekeepingGenes) + 3, df = 5), col = 'red', lwd = 4)
points(log2(Mean_PositiveControlProbes) - 1, col = alpha('cyan2', .8), pch = 18, cex = 2.5)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_PositiveControlProbes) - 1, df = 5), col = 'cyan1', lwd = 4)
points(log2(Mean_NegativeControlProbes), col = alpha('green2', .6), pch = 17, cex = 1.8)
lines(smooth.spline(c(1:length(LibrarySize)), log2(Mean_NegativeControlProbes), df = 5), col = 'green2', lwd = 4)
box(lwd = 5, bty = 'l')
rm(X, GradiantColors, Mean_NegativeControlProbes,
   Mean_PositiveControlProbes, Mean_HousekeepingGenes,
   LibrarySize)


#***** Log ratio between all pairs of duplicated samples
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) 

LogRatio_TechRep_RawCounts <- vector()
for(i in 1:1){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[i]
  RepData <- RawCounts_log [ , index]
  LogRatio <- as.data.frame(RepData[ , 1] - RepData[ , 2] )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep( i , 71)
  LogRatio_TechRep_RawCounts <- rbind(LogRatio_TechRep_RawCounts , LogRatio)
  rm(i, index, RepData, LogRatio)
}
nrow(LogRatio_TechRep_RawCounts)/71 # 17
LogRatio_TechRep_RawCounts$Datasets <- 'Unnormalized'




##################################################################################################################################
############################################### RUV-III normalization - using technical replicates and control genes #############

#***** Creating replicate matrix
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133

### Making sure that every row has got only one number
par(mfrow = c(2,1))
barplot(colSums(ReplicateMatrix))
barplot(rowSums(ReplicateMatrix))
par(mfrow = c(1,1))


#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:50, ] + 1))
RUVcorrected <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:50))
RUVcorrected <- t(RUVcorrected)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 2)
RUVcorrected <- t(RUVcorrected)
dim(RUVcorrected)
# We tried different numbers of k based on our positive controls####
all(colnames(RUVcorrected) == Nano_SampleInfo$SampleNames) ## TRUE


#***** RLE plots - Figure 1 A, RUV-III normalization
par(mar = c(6.5,6.5,2.3,0))
boxplot(RUVcorrected - rowMedians(RUVcorrected), main = '', xlab = '', ylab = '', xaxt = 'n', yaxt = 'n', ylim = c(-4.1,4.1),
        outline = FALSE, names = FALSE, frame = FALSE, whisklty = 3, whisklwd = 1.5, staplelty = 1, notch = TRUE, boxlwd = 2,
        staplelwd = 0 , boxcol = Color_Batches[factor(Nano_SampleInfo$cartridge)],
        border = Color_Batches[factor(Nano_SampleInfo$cartridge)], col = 'gray87')
box(lwd = 7, bty = 'l')
title('RUV-III normalized', line = -2, cex.main = 3.5)
Median_RUV <- apply(RUVcorrected - rowMedians(RUVcorrected), 2, median)
points(c(1:ncol(RUVcorrected)), Median_RUV, col = Color_Batches[factor(Nano_SampleInfo$cartridge)], pch = 19, cex = 1.2)
axis(1, cex.axis = 1, at = c(1, seq(20,166,20)), cex.axis = 2.5, lwd.ticks = 6,  mgp = c(3.5,1.6,0))
axis(2, mgp = c(3.5,.9,0), lwd.ticks = 6, las = 1, cex.axis = 3)
mtext(expression(paste('Samples','(', 'n'[samples], '=', '162', ')')),1 ,line = 5, cex = 3)
mtext('RLE', 2, line = 3.5, cex = 3.5)
abline(h = 0, col = 'black', lwd = 5, lty = 2)


#***** Correlation between ERCC1 and RRM1 in cancer samples
RUVIII_CancerData <- RUVcorrected[ , Nano_SampleInfo$Tissues=="cancer_organoid"]
dim(RUVIII_CancerData) ## 587 150
BioCo_RUV <- cor.test(unlist(t(RUVIII_CancerData['SMAD9' , ])) , unlist(t(RUVIII_CancerData[ 'WARS1' , ])), method = "spearman")[[4]]
par(mar = c(5,5,2,1))
plot (RUVIII_CancerData[ "SMAD9", ], RUVIII_CancerData [ "WARS1" , ],
      las = 1, pch = 21, col = "cyan", bg = 'blue', lwd = 1.2,
      main = "RUV-III normalized", bty = "l", cex.main = 2, mgp = c(3.2,.8,0),
      cex.axis = 1.7, cex.lab = 1.5, cex = 2.5, lwd.ticks = 3, ylab = "" ,
      xlab = expression(paste(italic(RRM1) , " (", log[2] , " normalized counts" , ")")))
mtext(expression(paste(italic(ERCC1) , " (", log[2] , " normalized counts" , ")")), 2, line = 3, cex = 1.5)
title(paste('(r = ', round(BioCo_RUV, digits = 2), ')'), line = -.5, cex = 1.4)
box(lwd = 6, bty = "l")


#***** Log DIFFERENCE between technical duplicated - per the paper
### Assessing the perfromance of RUV-III using 'leave out one duplicate'
DuplicatedSamples <- tuplicate(Nano_SampleInfo$Patient.barcodes, 2)
length(DuplicatedSamples) # 17
LogRatio_TechRep_RUVIII <- vector()
dataRUV <- t(log2(Nano_RawCounts[1:51, ] +1))

for(l in 1:length(DuplicatedSamples)){
  index <- Nano_SampleInfo$Patient.barcodes == DuplicatedSamples[l]
  info <- Nano_SampleInfo
  info$Patient.barcodes[index] <- c('Rep1', 'Rep2')
  X <- length(info$Patient.barcodes)
  Y <- length(unique(info$Patient.barcodes))
  
  ReplicateMatrix <- matrix(0, nrow = X, ncol = Y)
  row.names(ReplicateMatrix) <- info$Patient.barcodes
  colnames(ReplicateMatrix) <- unique(info$Patient.barcodes)
  for(i in 1:Y){
    n <- colnames(ReplicateMatrix)[i]
    sa <- which(row.names(ReplicateMatrix)==n)
    for(j in 1:length(sa)){
      ReplicateMatrix [sa[j] , i] <- 1
    }
  }
  RUVcorrected_Data <- ruv::RUVIII(dataRUV , ReplicateMatrix , ctl = ControlGenes, k = 2)
  RUVcorrected_Data <- t(RUVcorrected_Data)
  index <- which(index)
  LogRatio <- as.data.frame( (RUVcorrected_Data[ , index[1]] ) - (RUVcorrected_Data[ , index[2]]) )
  colnames(LogRatio) <- 'LogRatio'
  LogRatio$Replicates <- rep(l , 51)
  LogRatio_TechRep_RUVIII <- rbind(LogRatio_TechRep_RUVIII , LogRatio)
  rm(i, index, info, X, Y, LogRatio)
  
}
nrow(LogRatio_TechRep_RUVIII)/51
LogRatio_TechRep_RUVIII$Datasets <- 'RUV-III normalized'


#***** Technical Replicate Agreement plot for unnormalized, Nanostring Normalization and RUV-III (leave out one technical replicate)
### Figure 1 B
TRAallNormalizations <- rbind(LogRatio_TechRep_RawCounts, LogRatio_TechRep_RUVIII)
TRAallNormalizations$Replicates <- as.factor(TRAallNormalizations$Replicates)
TRAallNormalizations$Datasets <- as.factor(TRAallNormalizations$Datasets)
TRAallNormalizations$Datasets  <- factor(TRAallNormalizations$Datasets , levels = c('Unnormalized','RUV-III normalized'))
ggplot(data = TRAallNormalizations) +
  geom_boxplot(aes(y = LogRatio, x = Replicates, fill = Datasets, color=Datasets), outlier.size = .5,
               position = position_dodge(width = .7),
               width = 1, alpha = 0.8, lwd = .7) +
  ylab('Log ratio')+ylim(c(-10,10)) +
  scale_color_manual(values = c('lightblue', 'royalblue', 'navy')) +
  scale_fill_manual(values = c('lightblue', 'royalblue', 'navy')) +
  theme_classic() +
  geom_hline(yintercept = 0, lty = 2, lwd = .6, col = 'red')+
  theme(axis.title = element_text(size = 25),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.line = element_line(size = 1.5),
        legend.title = element_text(size = 20, face = c('italic', 'bold')),
        legend.text = element_text(size = 20),
        legend.position = "top", legend.direction = "horizontal")



############################################FINAL NORMALIZATION with 117 genes###################################################
length(Nano_SampleInfo$Patient.barcodes) # 162
length(unique(Nano_SampleInfo$Patient.barcodes)) # 135

ReplicateMatrix <- ruv::replicate.matrix(Nano_SampleInfo$Patient.barcodes)
dim(ReplicateMatrix) # 162 133
#***** Finding control genes
### Step 1: Using all genes as a set of negative control genes
# Performing RUVIII
dataRUV <- t(log2(Nano_RawCounts[1:51, ] +1))
RUVcorrected_organoid <- ruv::RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = c(1:51))
RUVcorrected_organoid <- t(RUVcorrected_organoid)

### Step 2: Selecting the most stable genes from step 1
LowVarGenes <- apply(RUVcorrected_organoid, 1, var)
ControlGenes <- which(LowVarGenes < .5)
length(ControlGenes) # 15 genes


### Step3: Performing RUV-III using the ControlGenes set
RUVcorrected_organoid <- RUVIII(Y = dataRUV, M = ReplicateMatrix, ctl = ControlGenes, k = 2)
RUVcorrected_organoid <- t(RUVcorrected_organoid)
dim(RUVcorrected_organoid)
# We tried different numbers of k based on our positive controls
all(colnames(RUVcorrected_organoid) == Nano_SampleInfo$SampleNames) ## TRUE


```
###TME RUVIII subtype
```{r}
log_nanostring_1 = RUVcorrected_organoid
```
```{r}
#Check if quantile normalization is required.
colramp = colorRampPalette(c(3,"white",2))(20)
plot(density(log_nanostring_1[,1]),col=colramp[1],lwd=1,ylim=c(0,.30), xlim=c(-20,20))
for(i in 2:9){lines(density(log_nanostring_1[,i]),lwd=1,col=colramp[i])}
#In the plot we can see that quantile normalization will aid in the data analysis
```

```{r}
housekeeping_genes = c("ACTB", "CTCF", "EIF4G", "HNRNPK", "RPL9", "SUMO3", "XRCC5")
normalizergenes = c(rntop50,housekeeping_genes)
```

```{r}
#Data sets - reduce to commongenes and transpose for FSQN
cancer_nanostring_1 <- subset(log_nanostring_1, rownames(log_nanostring_1) %in% as.matrix(rntop50))
cancer_nanostring_1 = t(cancer_nanostring_1)
```

```{r}
#FSQN the cancers

#TCGA FSQN to ACRG as reference due to predominate data derived from affymetrix platform and that TME clusters were established ACRG.
set.seed(99)   
target = as.matrix(log_ACRG_cancer)
test = as.matrix(cancer_nanostring_1)
classify_TME = quantileNormalizeByFeature(test, target)
```

```{r}
#Reduce to final genes

classify_TME <- classify_TME[, rntop50]
```
```{r}
#Classify the cancers according to TCGA 

predict.classify_TME = predict(tme.final,classify_TME)
predict.classify_TME_prob = predict(tme.final,classify_TME, type = "prob")

table(predict.classify_TME)
```
```{r}
#Extract calibrated probabilities 

predict.classify_TME_cal = predict(tme.final_calibration,predict.classify_TME_prob)
predict.classify_TME_prob_cal = predict(tme.final_calibration,predict.classify_TME_prob, type = "prob")
colnames(predict.classify_TME_prob_cal) = c("High_cal", "Low_cal")

TME_cal = as.data.frame(row.names(classify_TME))
TME_cal$TME_subtype_cal = predict.classify_TME_cal
colnames(TME_cal)[which(names(TME_cal) == "row.names(classify_TME)")] <- "sample_id"

TME_prob_cal = as.data.frame(row.names(classify_TME))
TME_prob_cal$High_cal = predict.classify_TME_prob_cal$High_cal
TME_prob_cal$Low_cal = predict.classify_TME_prob_cal$Low_cal
colnames(TME_prob_cal)[which(names(TME_prob_cal) == "row.names(classify_TME)")] <- "sample_id"
TME_ffpe = TME_prob_cal

TME_ffpe_names = Nano_SampleInfo
TME_ffpe_names = dplyr::select(TME_ffpe_names, c("Patient.barcodes","SampleNames"))

TME_ffpe = merge(TME_ffpe, TME_ffpe_names, by.x="sample_id", by.y="SampleNames")
TME_ffpe = TME_ffpe[,-1]
colnames(TME_ffpe)[which(names(TME_ffpe) == "Patient.barcodes")] <- "sample_id"


TME_ffpe %>% group_by(sample_id) %>% summarise_all(mean) %>% data.frame() -> TME_ffpe

TME_ffpe[,c(2:4)] = TME_ffpe[,c(2:3)] %>% mutate('TME_subtype'=names(.)[apply(., 1, which.max)])


```

```{r}
#Combine FFPE TCGA and TME

organoid_nanostring = merge(TCGA_ffpe,TME_ffpe, by="sample_id")

organoid_nanostring$tissue = "organoid"

gene_specific_nanostring = rbind(organoid_nanostring,ffpe_nanostring)
```

#Combo organoid and ffpe
```{r}

combo_nanostring = gene_specific_nanostring

write.csv(combo_nanostring, "combo_nanostring_67.csv")

combo_nanostring$cancer <- ifelse(grepl("C", combo_nanostring$sample_id, ignore.case = T), "Cancer", "Normal")
combo_nanostring_cancer = combo_nanostring[combo_nanostring$cancer=="Cancer",]

combo_nanostring_cancer$patient_id <- substr(combo_nanostring_cancer$sample_id, start = 1, stop = 2)

```
